### 2010-06-18 article.tex
Added article.tex

% Make two column format for LaTex 2e
\documentclass[10pt,twocolumn,a4paper]{article}

% Use the following packages
\usepackage{dcolumn}            % Align table columns on decimal point
\usepackage{graphicx}           % Include graphics
\usepackage{listings}           % Pretty source code listings
\usepackage{url}                % Handle URLs better

% Set dimensions of columns, gap between columns, and paragraph indent
\setlength{\textheight}{8.875in}
\setlength{\textwidth}{6.875in}
\setlength{\columnsep}{0.3125in}
\setlength{\topmargin}{0in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\parindent}{1pc}
\setlength{\oddsidemargin}{-.1875in}  % Centers text
\setlength{\evensidemargin}{-.1875in}

% Add the period after section numbers, and adjust spacing
\newcommand{\Section}[1]{\vspace{-8pt}\section{\hskip -1em.~~#1}\vspace{-3pt}}
\newcommand{\SubSection}[1]{\vspace{-3pt}\subsection{\hskip -1em.~~#1}
\vspace{-3pt}}

\begin{document}

% Make title bold
\title{\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche}

% Single author
\author{Bjorn Michelsen, III. Dan \\
  \texttt{<bjorn@bmichelsen.no>} \\
  \\
  ITF Tromsdalen School of Taekwon-Do \\
  Tromso, Norway
  }

% Print date
\date{\today}

% Produce the title
\maketitle

\section*{\centering Abstract}
\begin{em}
  Patterns in ITF Taekwon-Do are defined as a choreographed sequence of
  fundamental movements, which represents an attack or defense towards a
  particular target area or definite action of an attacker, against one or
  several imaginary opponents.

  These patterns are said to be using every available attacking and
  blocking tool from different directions\cite{cyclo:vol1}. It has,
  however, recently been observered that a right leg bias exist\cite{rlb}.

  A study of arm techniques in patterns Chon-Ji to Juche, initiated in the
  hope of uncovering whether or not there is a bias to either arm, is
  reported here.
\end{em}

% Approach, Results, Conclusion.

% Introduction
%   - Problem Statement
% Method
%   - Approach
% Results
%   - Tables
%   - Graphs
% Conclusions

%Problem definition
%Is there a bias towards the right or the left arm in ITF Taekwon-Do
%patterns Chon-Ji to Juche?

\Section{Introduction}

% mer utdypende fra 'abstract', ta med ting fra Right Leg Bias om
% nødvendig osv. sette dette under Previous Work?

Overall, there are a total of 152 kicks. 85 kicks are with the right
leg, and 67 kicks are with the left leg. This means that 56\% of all
kicks in patterns are with the right leg, whereas 44\% are with the left
leg.

% note that Gibb's article includes *all* the patterns

\SubSection{Previous Work}

There are various bibliographic and citation schemes available in
LaTex, but we choose to use the simplest one in this example.

\Section{Method}

How did you go about solving or making progress on the problem? Did you
use simulation, analytic models, prototype construction, or analysis of
field data for an actual product? What was the extent of your work (did
you look at one application program or a hundred programs in twenty
different programming languages?) What important variables did you
control, ignore, or measure?

\Section{Results}

What's the answer? Specifically, most good computer architecture papers
conclude that something is so many percent faster, cheaper, smaller, or
otherwise better than something else. Put the result there, in numbers.
Avoid vague, hand-waving results such as ``very'', ``small'', or
``significant.''

If you must be vague, you are only given license to do so when you can
talk about orders-of-magnitude improvement. There is a tension here in
that you should not provide numbers that can be easily misinterpreted,
but on the other hand you don't have room for all the caveats.

\Section{Conclusions}

What are the implications of your answer? Is it going to change the
world (unlikely), be a significant ``win'', be a nice hack, or simply
serve as a road sign indicating that this path is a waste of time (all
of the previous results are useful). Are your results general,
potentially generalizable, or specific to a particular case?

% Unnumbered section (note the asteriks)
\section*{Acknowledgments}

Thank you, thank you, thank you!

\begin{table}
  \centering
  \begin{tabular}{l|c|c} \hline \hline
    & Left Arm & Right Arm \\ \hline

    Blocks    & 148   & 133 \\
    Punches   &  60   &  71 \\
    Strikes   &  34   &  38 \\
    Thrusts   &  21   &  14 \\
    \hline

    \textbf{Total}   & \textbf{263}   & \textbf{256} \\
    \hline
  \end{tabular}
  \caption{Total number of techniques per arm by category.}
  %\label{tab:table1}
  \end{table}

\begin{table}
  \centering
  \begin{tabular}{l|c|c|c} \hline \hline
    & High & Middle & Low \\ \hline

    Blocks    & x   & y   & z \\
    Punches   & x   & y   & z \\
    Strikes   & x   & y   & z \\
    Thrusts   & x   & y   & z \\
    \hline

  \end{tabular}
  \caption{Total number of techniques by height.}
  %\label{tab:table1}
  \end{table}

\begin{table}
  \centering
  \begin{tabular}{l|c|c|c} \hline \hline
    & High & Middle & Low \\ \hline

    Blocks    & x   & y   & z \\
    Punches   & x   & y   & z \\
    Strikes   & x   & y   & z \\
    Thrusts   & x   & y   & z \\
    \hline

  \end{tabular}
  \caption{Total number of techniques by height and arm.}
  %\label{tab:table1}
  \end{table}

% percent more useful than numbers?

% References
\begin{thebibliography}{99}
    \small  % Use 9 point text

    \bibitem{cyclo:vol1}
      General Choi Hong Hi,
      {\emph Encyclopedia of Taekwon-Do}, Vol. 1, p. 13,
      International Taekwon-Do Federation, 1983.

    \bibitem{rlb}
      M. Gibb,
      {\emph Right Leg Bias in Patterns}, 2009.
      \url{http://visiontkd.co.uk/assetshome/pdf/Rightlegbias.pdf}

%\bibitem{key:foo}
%I. M. Author,
%``Some Related Article I Wrote,''
%{\em Some Fine Journal}, Vol. 17, pp. 1-100, 1987.

%\bibitem{foo:baz}
%A. N. Expert,
%{\em A Book He Wrote,}
%His Publisher, 1989.

\end{thebibliography}

\end{document}

### 2010-06-19 article.tex
Fixed emphasis on reference list
Started the Intruduction section, and added ideas for the rest of the article

@@
 \begin{em}
-  Patterns in ITF Taekwon-Do are defined as a choreographed sequence of
-  fundamental movements, which represents an attack or defense towards a
-  particular target area or definite action of an attacker, against one or
-  several imaginary opponents.
+  Patterns in International Taekwon-Do Federation (ITF) are defined as a
+  choreographed sequence of fundamental movements, which represents an attack
+  or defense towards a particular target area or definite action of an
+  attacker, against one or several imaginary opponents.
 
-  These patterns are said to be using every available attacking and
-  blocking tool from different directions\cite{cyclo:vol1}. It has,
-  however, recently been observered that a right leg bias exist\cite{rlb}.
+  These patterns are said to be using every available attacking and blocking
+  tool from different directions\cite{cyclo:vol1}. It has, however, recently
+  been observered that a right leg bias exist\cite{rlb}.
 
-  A study of arm techniques in patterns Chon-Ji to Juche, initiated in the
-  hope of uncovering whether or not there is a bias to either arm, is
-  reported here.
+  A study of arm techniques in patterns Chon-Ji to Juche, initiated in the hope
+  of uncovering whether or not there is a bias to either arm, is reported here.
 \end{em}
 
-% Approach, Results, Conclusion.
-
-% Introduction
-%   - Problem Statement
 % Method
 %   - Approach
+%   - Collecting data
+%   - Analysis of data
+%   - Uncertainty
 % Results
@@
 \Section{Introduction}
+A \emph{pattern} is a series of predefined basic elements called fundamental
+movements. The \emph{fundamental movements} are attack or defensive techniques
+against a specific target area or a predetermined action of an attacker.
 
-% mer utdypende fra 'abstract', ta med ting fra Right Leg Bias om
-% nødvendig osv. sette dette under Previous Work?
+Combined in a pattern, the student systematically deals with several imaginary
+opponents under various assumptions, using every available attacking and
+blocking tool from different directions\cite{cyclo:vol1}.
+
+% incorporate the problem statement within the Introduction instead of using
+% its own subsection
+
+\SubSection{Problem Statement}
+% pp. 154-155
+% given the weight/importance of fundamental movements and patterns in the encyclopedia
+% with approximately 3,200 techniques and
+%Patterns, therefore,
+%are the technical identity of Taekwon-Do.
+% The following points should be considered while performing patterns:
+%
+%   9. Attack and defense techniques should be equally
+%      distributed among right and left hands and feet
+%
+% and
+%
+% 'using every available attacking and blocking tool from different
+% directions..'
+%
+% and the recent discovery of the right leg bias,
+%
+% note that Gibb's article includes *all* the patterns
 
@@
 leg.
-
-% note that Gibb's article includes *all* the patterns
-
-\SubSection{Previous Work}
-
-There are various bibliographic and citation schemes available in
-LaTex, but we choose to use the simplest one in this example.
 
@@
     \bibitem{cyclo:vol1}
-      General Choi Hong Hi,
-      {\emph Encyclopedia of Taekwon-Do}, Vol. 1, p. 13,
-      International Taekwon-Do Federation, 1983.
+      Gen. Choi Hong Hi,
+      \emph{Encyclopedia of Taekwon-Do}, Vol. 1, p. 154,
+      International Taekwon-Do Federation, 1993.
 
@@
       M. Gibb,
-      {\emph Right Leg Bias in Patterns}, 2009.
+      \emph{Right Leg Bias in Patterns}, 2009.
       \url{http://visiontkd.co.uk/assetshome/pdf/Rightlegbias.pdf}

### 2010-07-04 article.tex
Added outline and moved around the sections

@@
+% Introduction
+%   Definitions
+%     Patterns
+%     Fundamental movements
+%     Groups of techniques
+%       blocks
+%       strikes
+%       thrusts
+%       punches
+%     Tagging
+%  Problem statement
+
+% Method
+%   Approach
+%   Collecting data
+%   Analysis of data
+%   Tagging
+%     Group of tags || Kind of Tags
+%       height
+%       weapon
+%       type etc.
+%    Difficulties related to tagging
+%  Uncertainty
+%
+% Results
+%   Tables
+%   Graphs
+% Conclusion
+
+%Related work
+%  Right Leg Bias
+
 % Make two column format for LaTex 2e
@@
 
-% Make title bold
+% Make the title bold
 \title{\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche}
 
-% Single author
+% Author information
 \author{Bjorn Michelsen, III. Dan \\
@@
 \begin{em}
+
+%An academic abstract typically outlines four elements germane to the completed work:
+
+    %* The research focus (i.e. statement of the problem(s)/research issue(s) addressed);
+    %* The research methods used (experimental research, case studies, questionnaires, etc.);
+    %* The results/findings of the research; and
+    %* The main conclusions and recommendations
+
+  % see the article: The Structure of Collaborative Tagging Systems
+  % located in ~/tmp/tags.pdf
+
+  Todo.
+\end{em}
+
+The Left Arm Bias in Taekwon-Do Patterns Chon-Ji to Juche
+
+\Section{Introduction}
+
 Patterns in International Taekwon-Do Federation (ITF) are defined as a
@@
 of uncovering whether or not there is a bias to either arm, is reported here.
-\end{em}
 
-% Method
-%   - Approach
-%   - Collecting data
-%   - Analysis of data
-%   - Uncertainty
-% Results
-%   - Tables
-%   - Graphs
-% Conclusions
-
-%Problem definition
-%Is there a bias towards the right or the left arm in ITF Taekwon-Do
-%patterns Chon-Ji to Juche?
-
-\Section{Introduction}
 A \emph{pattern} is a series of predefined basic elements called fundamental
@@
 
-% incorporate the problem statement within the Introduction instead of using
-% its own subsection
-
-\SubSection{Problem Statement}
+% Problem Statement
+%
 % pp. 154-155
@@
 %
+% Is there a bias towards the right or the left arm in ITF Taekwon-Do
+% patterns Chon-Ji to Juche?
+%
 % note that Gibb's article includes *all* the patterns
@@
 control, ignore, or measure?
+
+% Tagging can be defined as the practice of creating and
+% managing labels that categorize content using simple
+% keywords.
 
@@
 
-% Unnumbered section (note the asteriks)
+% Unnumbered section (note the '*')
 \section*{Acknowledgments}
 
-Thank you, thank you, thank you!
+  Todo.
 

### 2010-07-07 article.tex
Beginning of introduction, and added utf-8 support

@@
 %     Fundamental movements
+%  Related work
+%  Problem statement
 %     Groups of techniques
@@
 %     Tagging
-%  Problem statement
 
@@
 % Use the following packages
+\usepackage[utf8]{inputenc}     % Support for UTF-8
 \usepackage{dcolumn}            % Align table columns on decimal point
@@
 % Author information
-\author{Bjorn Michelsen, III. Dan \\
+\author{Bjørn Michelsen, III. Dan \\
   \texttt{<bjorn@bmichelsen.no>} \\
@@
   ITF Tromsdalen School of Taekwon-Do \\
-  Tromso, Norway
+  Tromsø, Norway
   }
@@
 
-The Left Arm Bias in Taekwon-Do Patterns Chon-Ji to Juche
-
 \Section{Introduction}
 
-Patterns in International Taekwon-Do Federation (ITF) are defined as a
-choreographed sequence of fundamental movements, which represents an attack
-or defense towards a particular target area or definite action of an
-attacker, against one or several imaginary opponents.
+  A \emph{pattern} in International Taekwon-Do Federation (ITF) is defined as
+  a choreographed sequence of fundamental movements. These \emph{fundamental
+  movements} are basic elements which represent an attack or defense towards a
+  specific target area, or a predetermined action of an attacker.
 
-These patterns are said to be using every available attacking and blocking
-tool from different directions\cite{cyclo:vol1}. It has, however, recently
-been observered that a right leg bias exist\cite{rlb}.
+  Combined in a pattern, it allows the student to systematically deal with one
+  or several imaginary opponents under various assumptions, using every
+  available attacking and blocking tool from different directions. In
+  addition, the techniques should also be evenly distributed between the left
+  and the right side\cite{cyclo:vol1}.
 
-A study of arm techniques in patterns Chon-Ji to Juche, initiated in the hope
-of uncovering whether or not there is a bias to either arm, is reported here.
+  It has, however, recently been observed that a bias towards the right leg
+  exist\cite{rlb}. % ALL patterns..
 
-A \emph{pattern} is a series of predefined basic elements called fundamental
-movements. The \emph{fundamental movements} are attack or defensive techniques
-against a specific target area or a predetermined action of an attacker.
+% how is related work written about?
 
-Combined in a pattern, the student systematically deals with several imaginary
-opponents under various assumptions, using every available attacking and
-blocking tool from different directions\cite{cyclo:vol1}.
+% recent studies of a right leg bias; Recent work has found that..
+%
+% in this paper, therefore, we analyze..
+
+%It has, however, recently been observed that a right leg bias
+%exist\cite{rlb} when looking at all the 24 Taekwon-Do patterns.
+
+% Is there a bias towards the *right* leg in Chon-Ji to Juche?
+
+%A study of arm techniques in patterns Chon-Ji to Juche, initiated in the hope
+%of uncovering whether or not there is a bias to either arm, is reported here.
 
@@
 % pp. 154-155
-% given the weight/importance of fundamental movements and patterns in the encyclopedia
-% with approximately 3,200 techniques and
-%Patterns, therefore,
-%are the technical identity of Taekwon-Do.
+%
 % The following points should be considered while performing patterns:
@@
 %
-% and
 %
-% 'using every available attacking and blocking tool from different
-% directions..'
 %
@@
 
-Overall, there are a total of 152 kicks. 85 kicks are with the right
-leg, and 67 kicks are with the left leg. This means that 56\% of all
-kicks in patterns are with the right leg, whereas 44\% are with the left
-leg.
+%Overall, there are a total of 152 kicks. 85 kicks are with the right
+%leg, and 67 kicks are with the left leg. This means that 56\% of all
+%kicks in patterns are with the right leg, whereas 44\% are with the left
+%leg.
 
@@
 
+  % Odd-Magne Hansen for helping me with the terminology, and general feedback
   Todo.
@@
       Gen. Choi Hong Hi,
-      \emph{Encyclopedia of Taekwon-Do}, Vol. 1, p. 154,
+      \emph{Encyclopedia of Taekwon-Do}, Vol. 1,
       International Taekwon-Do Federation, 1993.
@@
 
-%\bibitem{key:foo}
-%I. M. Author,
-%``Some Related Article I Wrote,''
-%{\em Some Fine Journal}, Vol. 17, pp. 1-100, 1987.
-
-%\bibitem{foo:baz}
-%A. N. Expert,
-%{\em A Book He Wrote,}
-%His Publisher, 1989.
-
 \end{thebibliography}

### 2010-07-10 article.tex
Added in-text reference

@@
   or several imaginary opponents under various assumptions, using every
-  available attacking and blocking tool from different directions. In
-  addition, the techniques should also be evenly distributed between the left
-  and the right side\cite{cyclo:vol1}.
+  available attacking and blocking tool from different
+  directions\cite{cyclo:vol1}. In addition, the techniques should also be
+  evenly distributed between the left and the right side\cite{cyclo:vol1}.
 

### 2010-07-14 article.tex
Added text to the introduction and tags section

--- 2010-07-07 article.tex
@@
-% Introduction
-%   Definitions
-%     Patterns
-%     Fundamental movements
-%  Related work
-%  Problem statement
-%     Groups of techniques
-%       blocks
-%       strikes
-%       thrusts
-%       punches
-%     Tagging
-
 % Method
-%   Approach
-%   Collecting data
-%   Analysis of data
-%   Tagging
-%     Group of tags || Kind of Tags
-%       height
-%       weapon
-%       type etc.
+%   Analysis of data || Processing
 %    Difficulties related to tagging
@@
 % Conclusion
-
-%Related work
-%  Right Leg Bias
 
@@
   a choreographed sequence of fundamental movements. These \emph{fundamental
-  movements} are basic elements which represent an attack or defense towards a
+  movements} are basic elements which represent an attack or defense against a
   specific target area, or a predetermined action of an attacker.
@@
   or several imaginary opponents under various assumptions, using every
-  available attacking and blocking tool from different directions. In
-  addition, the techniques should also be evenly distributed between the left
-  and the right side\cite{cyclo:vol1}.
+  available attacking and blocking tool from different directions.
+  Furthermore, the techniques should also be evenly distributed between the
+  left and the right side\cite{cyclo:vol1}.
 
   It has, however, recently been observed that a bias towards the right leg
-  exist\cite{rlb}. % ALL patterns..
+  exist. The study by Gibbs\cite{rlb} show that there is a total of 152 kicks
+  in patterns Chon-Ji to Tong-Il. 85 kicks are with the right leg, and 67
+  kicks are with the left leg. This means that 56\% of the kicks are with the
+  right leg, and 44\% with the left leg.
 
-% how is related work written about?
+  The work by Gibbs focused on kicks in all patterns, whereas this article
+  examines patterns Chon-Ji to Juche. Looking at kicks in said patterns using
+  Gibbs' paper, we find that there are 72 kicks in total. 42 kicks are with
+  the right leg, and 30 kicks are with the left leg. Roughly 58\% of the kicks
+  are with the right leg, and about 42\% with the left. Thus, the right leg
+  bias still holds.
 
-% recent studies of a right leg bias; Recent work has found that..
+  In this article, therefore, we analyze hand techniques in patterns Chon-Ji
+  to Juche using tags and report our findings of a left arm bias.
+
+\SubSection{Tags and Tagging}
+
+%   Applying tags (to dataset)
+%   Tagging
+%     Group of tags
+%     Groups of techniques {blocks, strikes, thrusts, punches}
+%       height
+%       weapon
+%       type etc.
+
+  In a hierarchical and exclusive classification system, each object belong in
+  one unambiguous category, which in turn is within another more general one.
+  Take the hierarchy of folders in a computer file system, for example. If we
+  want to organize articles on birds native to Africa in a directory, we have
+  several options:
+
+  \begin{lstlisting}
+    1. ~/articles/birds
+    2. ~/articles/africa
+    3. ~/articles/africa/birds
+    4. ~/articles/birds/africa
+  \end{lstlisting}
+
+  all articles on birds
+  all articles on africa
+  all articles on african birds
+  all articles on birds from africa
+
+  How we choose to organize the folders reflects a decision concerning the
+  relative importance of each characteristic\cite{golder:ct}. Folder names and
+  levels are in themselves informative, in that, like tags, they describe the
+  information held within them\cite{jones:folders}.
+
+% go through different folder setup
+% then insert the text about ``Tags, on the other hand..''
+% elaborate what it means that an object can have many tags
+% show a venn diagram
+% explain the venn diagram
+
+  Tags, on the other hand, are \emph{non-hierarchical} and \emph{inclusive},
+  which is to say that an object can be associated with a great variety of
+  tags simultaneously\cite{golder:ct}.
+
+  % Finally we can define tags as being non-hierarchical..
+  \emph{Tags} are non-hierarchical descriptive terms, keywords or labels that
+  is attached to an object for later
+  retrieval\cite{golder:ct}\cite{huang:tt}\cite{shirky:ontology}\cite{wikipedia:tags}.
+
+  %(mention polyhierarchical from the IA book)
+
+  %Descriptive terms, keywords or labels are metadata associated with a given
+  %object used to describe a concept or type of information\cite{heymann:ccch}.
+
+  %Object.. (define an object, then say that in this article an object is a
+  %pattern movement || a movement in a pattern)
+
+  %Later retrieval..
+
+% what does this all mean?
+%   non-hierarchical
+%   descriptive terms, keywords or labels
+%   object (a movement in a pattern)
+
+% Why do we tag?
+%   this kind of metadata helps describe an item
+%   allows it to be found again by searching
+%   future navigation, filtering or search
+%   later retrieval
+%   categorize content using keywords
+%   grouping related objects
+%   classifies
+%   organize
+%   for the purpose of classification and retrieval
+% How do we tag (tagging)?
+%   define tagging
+
+%\emph{Tagging} can be defined as the practice of creating and managing labels
+%that categorize content using simple keywords
+
+Tagging is the act of organizing a collection of entities, whether things or
+concepts, into related groups\cite{shirky:ontology}.
+
+\Section{Method}
+  Write introduction.
+
+% Three parts
+%   1. terminology (sonkal.taekwondo.cz)
+%   2. english description (condensed encyclopedia)
+%   3. tagging (how is tagging used? what is its role?)
+
+\SubSection{The Data}
+
+  Our data comes from two different sources. The terminology associated with
+  movements are from Taekwon-Do ITF Sonkal
+  Praha\footnote{\url{http://sonkal.taekwondo.cz}}, and the English
+  description of each movement is from the condensed
+  encyclopedia\cite{cyclo:con}.
+
+\SubSection{Approach}
+% collecting data
+
+  Todo.
+
+% registered terminology to all pattern movements, grouped by pattern names, including their pattern movement number, and motion type (normal, slow, etc.), link to movements_all.txt ?
+%   reviewed the terminology and movement type with odd-magne using a wiki
+%   made a few changes (corrected terminology for punch for instance)
+% added english description from the condensed encyclopedia to pattern
+%   checked that the terminology corresponded to the actual pattern movement
+% added tags
+%   (documented the tagging process)
+%   give an overview over (groups of) tags, see movements_with_tags.txt
+% divided each pattern into its own text file
+% modelled the project in the database (./models)
+%   explain all attributes etc.
+% made a ruby script to parse the text files (link to bootstrap.rb ?)
+%   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
+%   saving the data into an sqlite3 database for analysis
 %
-% in this paper, therefore, we analyze..
-
-%It has, however, recently been observed that a right leg bias
-%exist\cite{rlb} when looking at all the 24 Taekwon-Do patterns.
-
-% Is there a bias towards the *right* leg in Chon-Ji to Juche?
-
-%A study of arm techniques in patterns Chon-Ji to Juche, initiated in the hope
-%of uncovering whether or not there is a bias to either arm, is reported here.
-
-% Problem Statement
-%
-% pp. 154-155
-%
-% The following points should be considered while performing patterns:
-%
-%   9. Attack and defense techniques should be equally
-%      distributed among right and left hands and feet
+% show an example (chon-ji movement no. 1, for instance)
 %
@@
 %
-% and the recent discovery of the right leg bias,
+% The terminology to all pattern movements where first inserted into a text
+% file, along with.. || including..
 %
-% Is there a bias towards the right or the left arm in ITF Taekwon-Do
-% patterns Chon-Ji to Juche?
-%
-% note that Gibb's article includes *all* the patterns
 
-%Overall, there are a total of 152 kicks. 85 kicks are with the right
-%leg, and 67 kicks are with the left leg. This means that 56\% of all
-%kicks in patterns are with the right leg, whereas 44\% are with the left
-%leg.
-
-\Section{Method}
-
-How did you go about solving or making progress on the problem? Did you
-use simulation, analytic models, prototype construction, or analysis of
-field data for an actual product? What was the extent of your work (did
-you look at one application program or a hundred programs in twenty
-different programming languages?) What important variables did you
-control, ignore, or measure?
-
-% Tagging can be defined as the practice of creating and
-% managing labels that categorize content using simple
-% keywords.
+% hva forholder jeg meg til ved utvetydigheter (15-binds vs. *kondenserte*)
+% vurderinger på teknikker
+% hvorfor er tekniker gruppert slik de er?
 
@@
 
-What's the answer? Specifically, most good computer architecture papers
-conclude that something is so many percent faster, cheaper, smaller, or
-otherwise better than something else. Put the result there, in numbers.
-Avoid vague, hand-waving results such as ``very'', ``small'', or
-``significant.''
+%What's the answer? Specifically, most good computer architecture papers
+%conclude that something is so many percent faster, cheaper, smaller, or
+%otherwise better than something else. Put the result there, in numbers.
+%Avoid vague, hand-waving results such as ``very'', ``small'', or
+%``significant.''
 
-If you must be vague, you are only given license to do so when you can
-talk about orders-of-magnitude improvement. There is a tension here in
-that you should not provide numbers that can be easily misinterpreted,
-but on the other hand you don't have room for all the caveats.
+%If you must be vague, you are only given license to do so when you can
+%talk about orders-of-magnitude improvement. There is a tension here in
+%that you should not provide numbers that can be easily misinterpreted,
+%but on the other hand you don't have room for all the caveats.
+
+% Observation: Kicks happen between stances
 
@@
 
-What are the implications of your answer? Is it going to change the
-world (unlikely), be a significant ``win'', be a nice hack, or simply
-serve as a road sign indicating that this path is a waste of time (all
-of the previous results are useful). Are your results general,
-potentially generalizable, or specific to a particular case?
+%What are the implications of your answer? Is it going to change the
+%world (unlikely), be a significant ``win'', be a nice hack, or simply
+%serve as a road sign indicating that this path is a waste of time (all
+%of the previous results are useful). Are your results general,
+%potentially generalizable, or specific to a particular case?
 
@@
 
+  % Thanks to Master Nicolaisen for pointing out that I allredy had found a
+  % problem statement when I was still looking for one
+  %
   % Odd-Magne Hansen for helping me with the terminology, and general feedback
@@
 
+    \bibitem{cyclo:con}
+      Gen. Choi Hong Hi,
+      \emph{Taekwon-Do (the Korean Art of Self-Defence)}, Fifth Edition,
+      International Taekwon-Do Federation, 1999.
+
     \bibitem{rlb}
@@
 
+    \bibitem{golder:ct}
+      Scott A. Golder, Bernardo A. Huberman,
+      \emph{The Structure of Collaborative Tagging Systems}, 2005.
+      \url{http://www.hpl.hp.com/research/scl/papers/tags/tags.pdf}
+
+    \bibitem{heymann:ccch}
+      Paul Heymann, Hector Garcia-Molina,
+      \emph{Collaborative Creation of Communal Hierarchical Taxonomies in
+      Social Tagging Systems}, 2006.
+      \url{http://ilpubs.stanford.edu:8090/775/1/2006-10.pdf}
+
+    \bibitem{huang:tt}
+      Jeff Huang, Katherine M. Thornton, Efthimis N. Efthimiadis,
+      ``Conversational Tagging in Twitter,''
+      \emph{Hypertext}, pp. 173-177, 2010.
+
+    \bibitem{jones:folders}
+      William Jones, Ammy J. Phuwanartnurak, Rajdeep Gill, Harry Bruce,
+      \emph{Don't Take My Folders Away! Organizing Personal Information to Get
+      Things Done}, 2005.
+      \url{https://dlib.lib.washington.edu/dspace/bitstream/handle/1773/2031/
+           Don%27t%20take%20my%20folders%20away%2c%20current.pdf?sequence=2}
+
+    \bibitem{shirky:ontology}
+      Clay Shirky,
+      \emph{Ontology is Overrated: Categories, Links, and Tags}, 2005.
+      \url{http://www.shirky.com/writings/ontology_overrated.html}
+
+    \bibitem{wikipedia:tags}
+      \emph{Tag (metadata)}, July 12, 2010. \\
+      \url{http://en.wikipedia.org/wiki/Tag}
+
 \end{thebibliography}

### 2010-07-15 article.tex
Added Venn diagram with Asymptote

@@
 \usepackage{graphicx}           % Include graphics
+\usepackage{asymptote}          % Vector graphics language
 \usepackage{listings}           % Pretty source code listings
@@
 \vspace{-3pt}}
+
+\begin{asydef}
+// Global Asymptote definitions can be put here.
+import three;
+usepackage("bm");
+texpreamble("\def\V#1{\bm{#1}}");
+// One can globally override the default toolbar settings here:
+// settings.toolbar=true;
+\end{asydef}
 
@@
 % explain the venn diagram
+
+\def\A{A}
+\def\B{\V{B}}
+
+%\begin{figure}
+\begin{center}
+\begin{asy}
+size(4cm,0);
+pen colour1=red;
+pen colour2=green;
+
+pair z0=(0,0);
+pair z1=(-1,0);
+pair z2=(1,0);
+real r=1.5;
+path c1=circle(z1,r);
+path c2=circle(z2,r);
+fill(c1,colour1);
+fill(c2,colour2);
+
+picture intersection=new picture;
+fill(intersection,c1,colour1+colour2);
+clip(intersection,c2);
+
+add(intersection);
+
+draw(c1);
+draw(c2);
+
+//draw("$\A$",box,z1);              // Requires [inline] package option.
+//draw(Label("$\B$","$B$"),box,z2); // Requires [inline] package option.
+draw("$A$",box,z1);            
+draw("$\V{B}$",box,z2);
+
+pair z=(0,-2);
+real m=3;
+margin BigMargin=Margin(0,m*dot(unit(z1-z),unit(z0-z)));
+
+draw(Label("$A\cap B$",0),conj(z)--z0,Arrow,BigMargin);
+draw(Label("$A\cup B$",0),z--z0,Arrow,BigMargin);
+draw(z--z1,Arrow,Margin(0,m));
+draw(z--z2,Arrow,Margin(0,m));
+
+shipout(bbox(0.25cm));
+\end{asy}
+%\caption{Venn diagram}\label{venn}
+\end{center}
+%\end{figure}
 

### 2010-07-16 article.tex
Completed section on Tags, plus minor refactoring

@@
 
-  % see the article: The Structure of Collaborative Tagging Systems
-  % located in ~/tmp/tags.pdf
-
   Todo.
@@
 
-\SubSection{Tags and Tagging}
-
-%   Applying tags (to dataset)
-%   Tagging
-%     Group of tags
-%     Groups of techniques {blocks, strikes, thrusts, punches}
-%       height
-%       weapon
-%       type etc.
+\SubSection{Tags}
 
@@
 
-  all articles on birds
-  all articles on africa
-  all articles on african birds
-  all articles on birds from africa
-
   How we choose to organize the folders reflects a decision concerning the
@@
 
-% go through different folder setup
-% then insert the text about ``Tags, on the other hand..''
-% elaborate what it means that an object can have many tags
-% show a venn diagram
-% explain the venn diagram
+  The directory structure of (1), and (2) make central the fact that the
+  folders are about ``birds'' and ``africa''. But, they don't tell anything
+  about the other category. In (3) and (4) the files are organized by both
+  categories, and show that there is a parent-child or sibling relationships
+  between the folder names\cite{mathes:folk}.
 
+  \emph{Tags}, on the other hand, are non-hierarchical descriptive terms,
+  keywords or labels that is attached to an object for later retrieval
+  \cite{golder:ct}\cite{huang:tt}\cite{shirky:ontology}\cite{wikipedia:tags}.
+
+  They are \emph{non-hierarchical} and \emph{inclusive}, which is to say that
+  an object can be associated with a great variety of tags
+  simultaneously\cite{golder:ct}. The \emph{descriptive terms},
+  \emph{keywords} or \emph{labels} are metadata connected to a given object
+  which describe a concept or type of information\cite{heymann:ccch}.
+
+\SubSection{Tagging}
+
+  Tagging is the act of organizing a collection of objects into related
+  groups\cite{shirky:ontology}.
+
+% Why do we tag?
+%   this kind of metadata helps describe an item
+%   allows it to be found again by searching
+%   future navigation, filtering or search
+%   later retrieval
+%   categorize content using keywords
+%   grouping related objects
+%   classifies
+%   organize
+%   for the purpose of classification and retrieval
+%   display venn diagram
+%   explain venn diagram
+% How do we tag (tagging)?
+%   define tagging
+
+% end the section with something like..
+% tags add metadata to an object
+% tagging groups objects
+% the reason for why we bother is because we want to find the objects again
+
+\SubSection{Retrieval}
+
+% explain how later retrieval is done by using the venn diagram
+
+% Venn diagram
 \def\A{A}
@@
 
-  Tags, on the other hand, are \emph{non-hierarchical} and \emph{inclusive},
-  which is to say that an object can be associated with a great variety of
-  tags simultaneously\cite{golder:ct}.
-
-  % Finally we can define tags as being non-hierarchical..
-  \emph{Tags} are non-hierarchical descriptive terms, keywords or labels that
-  is attached to an object for later
-  retrieval\cite{golder:ct}\cite{huang:tt}\cite{shirky:ontology}\cite{wikipedia:tags}.
-
-  %(mention polyhierarchical from the IA book)
-
-  %Descriptive terms, keywords or labels are metadata associated with a given
-  %object used to describe a concept or type of information\cite{heymann:ccch}.
-
-  %Object.. (define an object, then say that in this article an object is a
-  %pattern movement || a movement in a pattern)
-
-  %Later retrieval..
-
-% what does this all mean?
-%   non-hierarchical
-%   descriptive terms, keywords or labels
-%   object (a movement in a pattern)
-
-% Why do we tag?
-%   this kind of metadata helps describe an item
-%   allows it to be found again by searching
-%   future navigation, filtering or search
-%   later retrieval
-%   categorize content using keywords
-%   grouping related objects
-%   classifies
-%   organize
-%   for the purpose of classification and retrieval
-% How do we tag (tagging)?
-%   define tagging
-
-%\emph{Tagging} can be defined as the practice of creating and managing labels
-%that categorize content using simple keywords
-
-Tagging is the act of organizing a collection of entities, whether things or
-concepts, into related groups\cite{shirky:ontology}.
-
 \Section{Method}
@@
 %
+
+%   Tagging
+%     Group of tags
+%     Groups of techniques {blocks, strikes, thrusts, punches}
+%       height
+%       weapon
+%       type etc.
 
@@
 
+    \bibitem{mathes:folk}
+      Adam Mathes,
+      ``Folksonomies -- Cooperative Classification and Communication Through
+      Shared Metadata,''
+      \emph{Computer Mediated Communication, LIS590CMC}, 2004.
+
     \bibitem{shirky:ontology}

### 2010-07-18 article.tex
Added set theory and intro on methods

@@
   \emph{keywords} or \emph{labels} are metadata connected to a given object
-  which describe a concept or type of information\cite{heymann:ccch}.
+  that describes a concept or type of information\cite{heymann:ccch}.
 
@@
 
-  Tagging is the act of organizing a collection of objects into related
+  \emph{Tagging} is the act of organizing a collection of objects into related
   groups\cite{shirky:ontology}.
 
-% Why do we tag?
-%   this kind of metadata helps describe an item
-%   allows it to be found again by searching
-%   future navigation, filtering or search
-%   later retrieval
-%   categorize content using keywords
-%   grouping related objects
-%   classifies
-%   organize
-%   for the purpose of classification and retrieval
-%   display venn diagram
-%   explain venn diagram
-% How do we tag (tagging)?
-%   define tagging
+\SubSection{Set theory}
 
-% end the section with something like..
-% tags add metadata to an object
-% tagging groups objects
-% the reason for why we bother is because we want to find the objects again
+  The characteristics of tags make them excellent for future navigation,
+  filtering or search. An object which has been tagged contains a collection,
+  or a set, of tags.  Each tag is an element of the set. The order of elements
+  within the set is irrelevant, but each element can only occur once.
 
-\SubSection{Retrieval}
+  For example, $\{1,5,8\}$ denotes a set with three elements: 1, 5 and 8.
+  $\{5,8,1\}$ is the same set, since the order of the elements doesn't matter.
+  $\{1,1,1\}$, however, is not a valid set because the element 1 occurs
+  several times. Elements in a set can also contain strings, so $\{loons,
+  penguins, terns\}$ is a valid set.
 
-% explain how later retrieval is done by using the venn diagram
+% set operations
+
+% union, intersection
 
@@
 \Section{Method}
-  Write introduction.
 
-% Three parts
-%   1. terminology (sonkal.taekwondo.cz)
-%   2. english description (condensed encyclopedia)
-%   3. tagging (how is tagging used? what is its role?)
+  In this section we describe where the data originates, and then elaborate on
+  the approach taken to register and investigate the dataset.
 
@@
   Our data comes from two different sources. The terminology associated with
-  movements are from Taekwon-Do ITF Sonkal
-  Praha\footnote{\url{http://sonkal.taekwondo.cz}}, and the English
-  description of each movement is from the condensed
+  movements are from Taekwon-Do ITF Sonkal Praha\footnote{\url{http://sonkal.taekwondo.cz}},
+  and the English description of each movement is from the condensed
   encyclopedia\cite{cyclo:con}.
@@
 \SubSection{Approach}
-% collecting data
+% collecting data into text files
+% tagging (how is tagging used? what is its role?)
 
@@
 
-  % Thanks to Master Nicolaisen for pointing out that I allredy had found a
-  % problem statement when I was still looking for one
+  % Thanks to Master Nicolaisen (VII. Dan) for pointing out that I already had
+  % found a problem statement when I was still looking for one
   %
-  % Odd-Magne Hansen for helping me with the terminology, and general feedback
+  % Odd-Magne Hansen (III. Dan) for helping me with the terminology, and
+  % general feedback
   Todo.

### 2010-07-20 article.tex
Completed section on set theory

@@
 \SubSection{Set theory}
+  A \emph{set} is a collection of distinct objects. It is a plurality thought
+  of as a unit\cite{hausdorff:sets}. \emph{Set theory} is the branch of
+  mathematics that studies sets\cite{wikipedia:tags}.
 
-  The characteristics of tags make them excellent for future navigation,
-  filtering or search. An object which has been tagged contains a collection,
-  or a set, of tags.  Each tag is an element of the set. The order of elements
-  within the set is irrelevant, but each element can only occur once.
+  An object which has been tagged contains a collection, or a set, of tags.
+  Each tag is an element of the set. The order of elements within the set is
+  irrelevant, but each element can only occur once.
 
-  For example, $\{1,5,8\}$ denotes a set with three elements: 1, 5 and 8.
+  For example, $\{1,5,8\}$ is a set with three elements: 1, 5 and 8.
   $\{5,8,1\}$ is the same set, since the order of the elements doesn't matter.
   $\{1,1,1\}$, however, is not a valid set because the element 1 occurs
-  several times. Elements in a set can also contain strings, so $\{loons,
-  penguins, terns\}$ is a valid set.
+  repeatedly. Elements in a set can contain strings as well, so $\{loons,
+  terns, penguins\}$ is also a valid set.
 
-% set operations
+  We usually denote a set by a capital letter for reference purposes. For
+  instance, $S=\{1,5,8\}$.
 
-% union, intersection
+  $a \in S$ denotes that the object $a$ is a member of the set $S$. If $a$
+  is not a member of S, we write $a \not \in S$.
 
-% Venn diagram
-\def\A{A}
-\def\B{\V{B}}
+  The \emph{union} of two sets $S$ and $T$ is the set
 
-%\begin{figure}
+  \[
+    S \cup T = \{x:x \in S \: or \: x \in T\}
+  \]
+
+% Venn diagram, showing the union of two sets
+\def\S{S}
+\def\T{\V{T}}
+
 \begin{center}
@@
 fill(c1,colour1);
+fill(c2,colour1);
+
+picture intersection=new picture;
+fill(intersection,c1,colour1);
+clip(intersection,c2,colour1);
+
+add(intersection);
+
+draw(c1);
+draw(c2);
+
+draw("$S$",box,z1);            
+draw("$\V{T}$",box,z2);
+
+pair z=(0,-2);
+real m=3;
+margin BigMargin=Margin(0,m*dot(unit(z1-z),unit(z0-z)));
+
+draw(Label("$S\cup T$",0),z--z0,Arrow,BigMargin);
+draw(z--z1,Arrow,Margin(0,m));
+draw(z--z2,Arrow,Margin(0,m));
+
+shipout(bbox(0.25cm));
+\end{asy}
+\end{center}
+
+  This consists of those objects which lie in the set $S$ or in the set $T$,
+  or in both. So,
+
+  \[
+    \{1, 2, 3\} \cup \{3, 4, 5\} = \{1, 2, 3, 4, 5\}
+  \]
+
+  The \emph{intersection} of two sets $S$ and $T$ is the set
+
+  \[
+    S \cap T = \{x:x \in S \: and \: x \in T\}
+  \]
+
+% Venn diagram, showing the intersect of two sets
+\def\S{S}
+\def\T{\V{T}}
+
+\begin{center}
+\begin{asy}
+size(4cm,0);
+pen colour1=red;
+pen colour2=white;
+
+pair z0=(0,0);
+pair z1=(-1,0);
+pair z2=(1,0);
+real r=1.5;
+path c1=circle(z1,r);
+path c2=circle(z2,r);
+fill(c1,colour2);
 fill(c2,colour2);
@@
 picture intersection=new picture;
-fill(intersection,c1,colour1+colour2);
+fill(intersection,c1,colour1);
 clip(intersection,c2);
@@
 
-//draw("$\A$",box,z1);              // Requires [inline] package option.
-//draw(Label("$\B$","$B$"),box,z2); // Requires [inline] package option.
-draw("$A$",box,z1);            
-draw("$\V{B}$",box,z2);
+draw("$S$",box,z1);            
+draw("$\V{T}$",box,z2);
 
@@
 
-draw(Label("$A\cap B$",0),conj(z)--z0,Arrow,BigMargin);
-draw(Label("$A\cup B$",0),z--z0,Arrow,BigMargin);
+draw(Label("$S\cap T$",0),z--z0,Arrow,BigMargin);
+
+shipout(bbox(0.25cm));
+\end{asy}
+\end{center}
+
+  This consists of those objects which lie in both the set $S$ and the set
+  $B$. So,
+
+  \[
+    \{1, 2, 3\} \cap \{2, 3, 4\} = \{2, 3\}
+  \]
+
+  The \emph{complement} of a set $T$ relative to a set $S$ is the set
+
+  \[
+    S - T = \{x:x \in S \: and \: x \not \in T\}
+  \]
+
+% Venn diagram, showing the complement of two sets
+\def\S{S}
+\def\T{\V{T}}
+
+\begin{center}
+\begin{asy}
+size(4cm,0);
+pen colour1=red;
+pen colour2=white;
+
+pair z0=(0,0);
+pair z1=(-1,0);
+pair z2=(1,0);
+real r=1.5;
+path c1=circle(z1,r);
+path c2=circle(z2,r);
+fill(c1,colour1);
+fill(c2,colour2);
+
+picture intersection=new picture;
+fill(intersection,c1,colour2);
+clip(intersection,c2);
+
+add(intersection);
+
+draw(c1);
+draw(c2);
+
+draw("$S$",box,z1);            
+draw("$\V{T}$",box,z2);
+
+pair z=(0,-2);
+real m=3;
+margin BigMargin=Margin(0,m*dot(unit(z1-z),unit(z0-z)));
+
+draw(Label("$S - T$",0),z--z0,Arrow,BigMargin);
 draw(z--z1,Arrow,Margin(0,m));
@@
 \end{asy}
-%\caption{Venn diagram}\label{venn}
 \end{center}
-%\end{figure}
+
+  This consists of those objects which lie in the set $S$ but not in the set
+  $T$. So,
+
+  \[
+    \{1, 2, 3\} - \{2, 3, 4\} = \{1\}
+  \]
+
+  The \emph{symmetric difference} of the sets $S$ and $T$ is the set
+
+  \[
+    S \Delta T = \{x:(x \in S \: and \: x \not \in T) \: or \: (x \in T \: and
+    \: x \not \in S)\}
+  \]
+
+% Venn diagram, showing the symmetric difference of two sets
+\def\S{S}
+\def\T{\V{T}}
+
+\begin{center}
+\begin{asy}
+size(4cm,0);
+pen colour1=red;
+pen colour2=green;
+pen colour3=white;
+
+pair z0=(0,0);
+pair z1=(-1,0);
+pair z2=(1,0);
+real r=1.5;
+path c1=circle(z1,r);
+path c2=circle(z2,r);
+fill(c1,colour1);
+fill(c2,colour1);
+
+picture intersection=new picture;
+fill(intersection,c1,colour3);
+clip(intersection,c2);
+
+add(intersection);
+
+draw(c1);
+draw(c2);
+
+draw("$S$",box,z1);            
+draw("$\V{T}$",box,z2);
+
+pair z=(0,-2);
+real m=3;
+margin BigMargin=Margin(0,m*dot(unit(z1-z),unit(z0-z)));
+
+draw(Label("$S\cap T$",0),z--z0,Arrow,BigMargin);
+
+shipout(bbox(0.25cm));
+\end{asy}
+\end{center}
+
+  This consists of those objects which lie either in one of the sets, but not
+  in both. So,
+
+  \[
+    \{1, 2, 3\} - \{2, 3, 4\} = \{1, 4\}
+  \]
+
+% why does this matter? how is it applied to tags and tagging?
 
@@
     \bibitem{golder:ct}
-      Scott A. Golder, Bernardo A. Huberman,
+      S. A. Golder, B. A. Huberman,
       \emph{The Structure of Collaborative Tagging Systems}, 2005.
@@
     \bibitem{heymann:ccch}
-      Paul Heymann, Hector Garcia-Molina,
+      P. Heymann, H. Garcia-Molina,
       \emph{Collaborative Creation of Communal Hierarchical Taxonomies in
@@
 
+    \bibitem{hausdorff:sets}
+      F. Hausdorff,
+      \emph{Set theory},
+      Chelsea Publishing Company, 1991.
+
     \bibitem{huang:tt}
-      Jeff Huang, Katherine M. Thornton, Efthimis N. Efthimiadis,
+      J. Huang, K. M. Thornton, E. N. Efthimiadis,
       ``Conversational Tagging in Twitter,''
@@
     \bibitem{jones:folders}
-      William Jones, Ammy J. Phuwanartnurak, Rajdeep Gill, Harry Bruce,
+      W. Jones, A. J. Phuwanartnurak, R. Gill, H. Bruce,
       \emph{Don't Take My Folders Away! Organizing Personal Information to Get
@@
     \bibitem{mathes:folk}
-      Adam Mathes,
+      A. Mathes,
       ``Folksonomies -- Cooperative Classification and Communication Through
@@
     \bibitem{shirky:ontology}
-      Clay Shirky,
+      C. Shirky,
       \emph{Ontology is Overrated: Categories, Links, and Tags}, 2005.
@@
 
+    \bibitem{wikipedia:sets}
+      \emph{Set theory}, July 19, 2010. \\
+      \url{http://en.wikipedia.org/wiki/Set_theory}
+
     \bibitem{wikipedia:tags}
-      \emph{Tag (metadata)}, July 12, 2010. \\
+      \emph{Tag (metadata)}, July 19, 2010. \\
       \url{http://en.wikipedia.org/wiki/Tag}

### 2010-07-21 article.tex
Refactored diagrams into their own files

@@
 \begin{asydef}
-// Global Asymptote definitions can be put here.
+// Global Asymptote definitions
 import three;
@@
 texpreamble("\def\V#1{\bm{#1}}");
-// One can globally override the default toolbar settings here:
-// settings.toolbar=true;
 \end{asydef}
@@
   % Venn diagram, showing the union of two sets
-\def\S{S}
-\def\T{\V{T}}
-
-\begin{center}
-\begin{asy}
-size(4cm,0);
-pen colour1=red;
-pen colour2=green;
-
-pair z0=(0,0);
-pair z1=(-1,0);
-pair z2=(1,0);
-real r=1.5;
-path c1=circle(z1,r);
-path c2=circle(z2,r);
-fill(c1,colour1);
-fill(c2,colour1);
-
-picture intersection=new picture;
-fill(intersection,c1,colour1);
-clip(intersection,c2,colour1);
-
-add(intersection);
-
-draw(c1);
-draw(c2);
-
-draw("$S$",box,z1);            
-draw("$\V{T}$",box,z2);
-
-pair z=(0,-2);
-real m=3;
-margin BigMargin=Margin(0,m*dot(unit(z1-z),unit(z0-z)));
-
-draw(Label("$S\cup T$",0),z--z0,Arrow,BigMargin);
-draw(z--z1,Arrow,Margin(0,m));
-draw(z--z2,Arrow,Margin(0,m));
-
-shipout(bbox(0.25cm));
-\end{asy}
-\end{center}
+  \input{venn_union.asy}
 
@@
   % Venn diagram, showing the intersect of two sets
-\def\S{S}
-\def\T{\V{T}}
-
-\begin{center}
-\begin{asy}
-size(4cm,0);
-pen colour1=red;
-pen colour2=white;
-
-pair z0=(0,0);
-pair z1=(-1,0);
-pair z2=(1,0);
-real r=1.5;
-path c1=circle(z1,r);
-path c2=circle(z2,r);
-fill(c1,colour2);
-fill(c2,colour2);
-
-picture intersection=new picture;
-fill(intersection,c1,colour1);
-clip(intersection,c2);
-
-add(intersection);
-
-draw(c1);
-draw(c2);
-
-draw("$S$",box,z1);            
-draw("$\V{T}$",box,z2);
-
-pair z=(0,-2);
-real m=3;
-margin BigMargin=Margin(0,m*dot(unit(z1-z),unit(z0-z)));
-
-draw(Label("$S\cap T$",0),z--z0,Arrow,BigMargin);
-
-shipout(bbox(0.25cm));
-\end{asy}
-\end{center}
+  \input{venn_intersect.asy}
 
@@
   % Venn diagram, showing the complement of two sets
-\def\S{S}
-\def\T{\V{T}}
-
-\begin{center}
-\begin{asy}
-size(4cm,0);
-pen colour1=red;
-pen colour2=white;
-
-pair z0=(0,0);
-pair z1=(-1,0);
-pair z2=(1,0);
-real r=1.5;
-path c1=circle(z1,r);
-path c2=circle(z2,r);
-fill(c1,colour1);
-fill(c2,colour2);
-
-picture intersection=new picture;
-fill(intersection,c1,colour2);
-clip(intersection,c2);
-
-add(intersection);
-
-draw(c1);
-draw(c2);
-
-draw("$S$",box,z1);            
-draw("$\V{T}$",box,z2);
-
-pair z=(0,-2);
-real m=3;
-margin BigMargin=Margin(0,m*dot(unit(z1-z),unit(z0-z)));
-
-draw(Label("$S - T$",0),z--z0,Arrow,BigMargin);
-draw(z--z1,Arrow,Margin(0,m));
-draw(z--z2,Arrow,Margin(0,m));
-
-shipout(bbox(0.25cm));
-\end{asy}
-\end{center}
+  \input{venn_complement.asy}
 
@@
   % Venn diagram, showing the symmetric difference of two sets
-\def\S{S}
-\def\T{\V{T}}
-
-\begin{center}
-\begin{asy}
-size(4cm,0);
-pen colour1=red;
-pen colour2=green;
-pen colour3=white;
-
-pair z0=(0,0);
-pair z1=(-1,0);
-pair z2=(1,0);
-real r=1.5;
-path c1=circle(z1,r);
-path c2=circle(z2,r);
-fill(c1,colour1);
-fill(c2,colour1);
-
-picture intersection=new picture;
-fill(intersection,c1,colour3);
-clip(intersection,c2);
-
-add(intersection);
-
-draw(c1);
-draw(c2);
-
-draw("$S$",box,z1);            
-draw("$\V{T}$",box,z2);
-
-pair z=(0,-2);
-real m=3;
-margin BigMargin=Margin(0,m*dot(unit(z1-z),unit(z0-z)));
-
-draw(Label("$S\cap T$",0),z--z0,Arrow,BigMargin);
-
-shipout(bbox(0.25cm));
-\end{asy}
-\end{center}
+  \input{venn_difference.asy}
 

### 2010-07-23 article.tex
Finished section on data, minor refactoring

@@
-% Method
-%   Analysis of data || Processing
-%    Difficulties related to tagging
-%  Uncertainty
-%
-% Results
-%   Tables
-%   Graphs
-% Conclusion
-
 % Make two column format for LaTex 2e
@@
 \setlength{\parindent}{1pc}
-\setlength{\oddsidemargin}{-.1875in}  % Centers text
+\setlength{\oddsidemargin}{-.1875in}    % Centers the text
 \setlength{\evensidemargin}{-.1875in}
@@
 
+% Global Asymptote definitions
 \begin{asydef}
-// Global Asymptote definitions
 import three;
@@
 
+% Document
 \begin{document}
@@
 
+% Sections
 \section*{\centering Abstract}
@@
   \[
-    \{1, 2, 3\} - \{2, 3, 4\} = \{1, 4\}
+    \{1, 2, 3\} \Delta \{2, 3, 4\} = \{1, 4\}
   \]
-
-% why does this matter? how is it applied to tags and tagging?
 
@@
 
+  The terminology dataset is organized by pattern names. It contains a list of
+  all techniques in patterns Chon-Ji to Juche using terminology. It also
+  includes motion type on movements that are not performed in normal motion.
+  The file was reviewed and minor corrections were made to the terminology.
+
 \SubSection{Approach}
-% collecting data into text files
-% tagging (how is tagging used? what is its role?)
 
-  Todo.
+% the approach taken to register and investigate the dataset
 
-% registered terminology to all pattern movements, grouped by pattern names, including their pattern movement number, and motion type (normal, slow, etc.), link to movements_all.txt ?
-%   reviewed the terminology and movement type with odd-magne using a wiki
-%   made a few changes (corrected terminology for punch for instance)
-% added english description from the condensed encyclopedia to pattern
-%   checked that the terminology corresponded to the actual pattern movement
+% added English movement description from the condensed encyclopedia
 % added tags
-%   (documented the tagging process)
 %   give an overview over (groups of) tags, see movements_with_tags.txt
-% divided each pattern into its own text file
+%     Group of tags
+%     Groups of techniques {blocks, strikes, thrusts, punches}
+%       height
+%       weapon
+%       type etc.
+%   show an example (chon-ji movement no. 1, for instance)
+% divided each pattern into its own text file (./patterns/*)
 % modelled the project in the database (./models)
@@
 %
-% show an example (chon-ji movement no. 1, for instance)
-%
-%
-%
-% The terminology to all pattern movements where first inserted into a text
-% file, along with.. || including..
-%
 
 % Tagging
-%     Group of tags
-%     Groups of techniques {blocks, strikes, thrusts, punches}
-%       height
-%       weapon
-%       type etc.
+%   tagging (how is tagging used? what is its role?)
+%   connect set theory to tagging? how is it applied to tags and tagging?
 
@@
 % Observation: Kicks happen between stances
+% Tables
+% Graphs
 

### 2010-07-23 article.tex
Rewording of the intro to the data section

@@
   Our data comes from two different sources. The terminology associated with
-  movements are from Taekwon-Do ITF Sonkal Praha\footnote{\url{http://sonkal.taekwondo.cz}},
+  pattern movements is from Taekwon-Do ITF Sonkal Praha\footnote{\url{http://sonkal.taekwondo.cz}},
   and the English description of each movement is from the condensed
@@
   includes motion type on movements that are not performed in normal motion.
-  The file was reviewed and minor corrections were made to the terminology.
+
+  The English description to every movement was registered manually after
+  reviewing, and making minor corrections to, the terminology.
 
@@
 
-% added English movement description from the condensed encyclopedia
 % added tags

### 2010-07-25 article.tex
Removed unnecessary details from the outline
Added description and tags in the approach section

@@
   Our data comes from two different sources. The terminology associated with
-  pattern movements is from Taekwon-Do ITF Sonkal Praha\footnote{\url{http://sonkal.taekwondo.cz}},
-  and the English description of each movement is from the condensed
-  encyclopedia\cite{cyclo:con}.
+  pattern movements is from Taekwon-Do ITF Sonkal Praha\footnote{\url{http://
+  sonkal.taekwondo.cz}}, and the English description of each movement is from
+  the condensed encyclopedia\cite{cyclo:con}.
 
@@
 
-% the approach taken to register and investigate the dataset
+  Each pattern movement is tagged on the basis of their English description
+  from the condensed encyclopedia. In addition, suitable tags were attached to
+  the dataset while performing the pattern to add necessary details.
+
+  The first movement in Chon-Ji, for instance, is to ``[m]ove the left foot to
+  B, forming a left walking stance toward B while executing a low block to B
+  with the left forearm.'' Removing the unnecessary parts of the description,
+  we're left with:
+
+  \[
+    \{left \: walking \: stance, \: low \: block, \: left \: forearm\}
+  \]
+
+  Converting the above to tags gives us:
+
+  \[
+    \{walking\_stance, left\_stance, low\_technique, left\_technique,
+    block, forearm, outer\_forearm, normal\_motion\}
+  \]
+
+% why?
+%because it to tags means we need to be more specific, so it's easier to
+%retrieve movements of same qualities..
+
+% pek på forskjeller mellom tags og bevegelse, hvilke detaljer som blir
+% utelatt, detaljer i forhold til diagrammet er ikke tatt med i datasettet
+
+% techniques were grouped
+
+%stance[type, (side)], technique[height,
+
+%stance type, [stance side], technique height, technique side, [direction of
+%technique side], technique type, tool group, technique tool,
+%[specific technique tool], motion type
+
+%stance (type, [side]), technique (height, side, [direction], type), technique
+%(tool group, tool, [specific tool], motion type
+
+%stance type
+%stance side (left, right, none (sitting stances for example))
+%technique height
+%technique side (left, right or both)
+%[direction of technique (side_front)]
+%technique type (attack or block)
+%tool group (forearm, strike, thrust, punch)
+%technique tool (outer_forearm, rising_block, front_strike, finger, angle_punch)
+%specific technique tool, when needed (side_elbow, double_finger)
+%motion type (normal_motion, fast_motion)
+
+%ett eksempel med blokk, pluss ett eksempel med angrep (begge eksemplene bør få
+%med de aller fleste momentene nevnt over for å illustrere hva som menes med de
+%ulike gruppene)
 
@@
 %       type etc.
-%   show an example (chon-ji movement no. 1, for instance)
-% divided each pattern into its own text file (./patterns/*)
-% modelled the project in the database (./models)
-%   explain all attributes etc.
-% made a ruby script to parse the text files (link to bootstrap.rb ?)
-%   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
-%   saving the data into an sqlite3 database for analysis
-%
 
@@
 % vurderinger på teknikker
-% hvorfor er tekniker gruppert slik de er?
+
+% modelled the project in the database (./models)
+%   explain all attributes etc.
+% made a ruby script to parse the text files (link to bootstrap.rb ?)
+%   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
+%   saving the data into an sqlite3 database for analysis
+%
 

### 2010-08-09 article.tex
Minor re-wording in intro
Added text to the approach section

--- 2010-07-23 article.tex
@@
 \usepackage{url}                % Handle URLs better
+\usepackage{amsmath}            % Extend mathematical typesetting
 
@@
   In this article, therefore, we analyze hand techniques in patterns Chon-Ji
-  to Juche using tags and report our findings of a left arm bias.
+  to Juche using tags and then report our findings of a left arm bias.
 
@@
 
+% TODO: vurderinger på teknikker, se notater i wikien
+
 \SubSection{Approach}
 
-% the approach taken to register and investigate the dataset
+  Each pattern movement is tagged on the basis of their English description
+  from the condensed encyclopedia. In addition, suitable tags is attached to
+  the dataset while performing the pattern to add necessary detail.
 
-% added tags
-%   give an overview over (groups of) tags, see movements_with_tags.txt
-%     Group of tags
-%     Groups of techniques {blocks, strikes, thrusts, punches}
-%       height
-%       weapon
-%       type etc.
-%   show an example (chon-ji movement no. 1, for instance)
-% divided each pattern into its own text file (./patterns/*)
+  The first movement in Chon-Ji, for instance, is to ``[m]ove the left foot to
+  B, forming a left walking stance toward B while executing a low block to B
+  with the left forearm\cite{cyclo:vol1}.'' Removing the verbose parts of the
+  description we're left with:
+
+  \[
+    \{left \: walking \: stance, \: low \: block, \: left \: forearm\}
+  \]
+
+  Converting the above to tags gives us:
+
+  \begin{align*}
+    \{walking \: stance, \: left \: stance, \: low \: technique, \\
+    left \: technique, \: block, \: forearm, \: outer \: forearm, \\
+    normal \: motion\}
+  \end{align*}
+
+  Information about the stance type is presented first, followed by stance
+  side (left, right or none where applicable --- ie. sitting stance, technique
+  height (low, middle, high), technique side (left arm or right arm, can also
+  be both), direction of the technique (when needed), primary technique type
+  (attack, block, kick), technique group (punch, strike, thrust), tool group
+  (forearm, knife hand, finger etc.), tool (inner forearm, outer forearm,
+  double finger etc.), and finally motion type (normal motion, slow motion,
+  consecutive motion and so on).
+
+  Tagging movements in such a formalized manner enables us to retrieve the
+  data we're interested in, using concepts from set theory.
+
 % modelled the project in the database (./models)
@@
 %
-
-% Tagging
-%   tagging (how is tagging used? what is its role?)
-%   connect set theory to tagging? how is it applied to tags and tagging?
-
-% hva forholder jeg meg til ved utvetydigheter (15-binds vs. *kondenserte*)
-% vurderinger på teknikker
-% hvorfor er tekniker gruppert slik de er?
 

### 2010-08-12 article.tex
Added classification sub section to th eapproach

@@
 
-% TODO: vurderinger på teknikker, se notater i wikien
-
 \SubSection{Approach}
@@
 
-  Tagging movements in such a formalized manner enables us to retrieve the
-  data we're interested in, using concepts from set theory.
-
+  % FIXME add database and ruby script info here
   % modelled the project in the database (./models)
@@
   %
+
+  Tagging movements in such a formalized manner, and registering it in a
+  database, enables us to retrieve the data we're interested in using concepts
+  from set theory.
+
+\SubSection{Classification}
+
+% TODO: vurderinger på teknikker, se notater i wikien
+
+\begin{itemize}
+  \item
+    \emph{Yul-Gok Tul}
+    \begin{itemize}
+      \item
+        {\bf Movement 24}, \emph{Gunnun so ap palkup bandae taerigi}, is
+        tagged with $\{front\_strike\}$ due to the English description of
+        striking with the right front elbow.
+      \item
+        {\bf Movement 27}, \emph{Gunnun so ap palkup bandae taerigi}, is
+        tagged with $\{front\_strike\}$ due to the English description of
+        striking with the left front elbow.
+    \end{itemize}
+  \item
+    \emph{Joong-Gun Tul}
+    \begin{itemize}
+      \item
+        {\bf Movement 8}, \emph{Gunnun so wipalkup taerigi}, is tagged
+        $\{upper\_strike, \: upper\_elbow\}$ since the English description
+        says that the movement is ``a right upper elbow strike.''
+      \item
+        {\bf Movement 10}, \emph{Gunnun so wipalkup taerigi}, is tagged
+        $\{upper\_strike, \: upper\_elbow\}$ since the English description
+        says that the movement is ``a left upper elbow strike.''
+      \item
+        {\bf Movement 11}, \emph{Gunnun so sang sewo jirugi}, is tagged as a
+        left and right technique, with $\{left\_technique, \:
+        right\_technique\}$.
+      \item
+        {\bf Movement 12}, \emph{Gunnun so sang dwijibo jirugi}, is tagged as
+        a left and right technique, with $\{left\_technique, \:
+        right\_technique\}$.
+      \item
+        {\bf Movement 27}, \emph{Nachuo so sonbadak noollo makgi}, is tagged
+        as a $\{middle\_technique, \: low\_technique\}$ because the left hand
+        is in the middle section and the right hand, forming the pressing
+        block, is in the low section of the body. Furthermore, the movement
+        has been tagged as a $\{right\_technique, \: left\_technique\}$ to
+        reflect that both hands are being used.
+      \item
+        {\bf Movement 29}, \emph{Nachuo so sonbadak noollo makgi}, is tagged
+        as a $\{middle\_technique, \: low\_technique\}$ because the right hand
+        is in the middle section and the left hand, forming the pressing
+        block, is in the low section of the body. Furthermore, the movement
+        has been tagged as a $\{right\_technique, \: left\_technique\}$ to
+        reflect that both hands are being used.
+    \end{itemize}
+  \item
+    \emph{Choong-Moo Tul}
+    \begin{itemize}
+      \item
+        {\bf Movement 19
+    \end{itemize}
+  \item
+    \emph{Pragmatic}
+    \begin{itemize}
+      \item
+        Free software is available for experimentation and testing.
+      \item
+        Most readers of this text have a background in relational technology. 
+    \end{itemize}
+\end{itemize}
 

### 2010-08-14 article.tex
Added pattern movements to the classification section

@@
   Each pattern movement is tagged on the basis of their English description
-  from the condensed encyclopedia. In addition, suitable tags is attached to
+  from the condensed encyclopedia. In addition, suitable tags were attached to
   the dataset while performing the pattern to add necessary detail.
@@
   Information about the stance type is presented first, followed by stance
-  side (left, right or none where applicable --- ie. sitting stance, technique
-  height (low, middle, high), technique side (left arm or right arm, can also
-  be both), direction of the technique (when needed), primary technique type
-  (attack, block, kick), technique group (punch, strike, thrust), tool group
-  (forearm, knife hand, finger etc.), tool (inner forearm, outer forearm,
-  double finger etc.), and finally motion type (normal motion, slow motion,
-  consecutive motion and so on).
+  side (left, right or none where applicable --- ie. sitting stance),
+  technique height (low, middle, high), technique side (left arm or right arm,
+  can also be both), direction of the technique (when needed), primary
+  technique type (attack, block, kick), technique group (punch, strike,
+  thrust), tool group (forearm, knife hand, finger etc.), tool (inner forearm,
+  outer forearm, double finger etc.), and finally motion type (normal motion,
+  slow motion, consecutive motion and so on).
 
@@
 
-% TODO: vurderinger på teknikker, se notater i wikien
+% TODO: introduction
 
@@
   \item
-    \emph{Choong-Moo Tul}
+    \emph{Po-Eun Tul}
     \begin{itemize}
       \item
-        {\bf Movement 19
+        {\bf Movement 6}, \emph{Annun so ap joomuk noollo makgi}, consist of
+        two blocks. The first is a ``pressing block with the left fore fist,''
+        and the second one is a ``side front block with the right inner
+        forearm.'' When searching, this movement will only register as one
+        block.
+      \item
+        {\bf Movement 7}, \emph{Annun so ap joomuk noollo makgi}, consist of
+        two blocks. The first is a ``pressing block with the right fore
+        fist,'' and the second one is a ``side front block with the left inner
+        forearm.'' When searching, this movement will only register as one
+        block.
+      \item
+        {\bf Movement 24}, \emph{Annun so ap joomuk noollo makgi}, consist of
+        two blocks. The first is a ``pressing block with the right fore
+        fist,'' and the second one is a ``side front block with the left inner
+        forearm.'' When searching, this movement will only register as one
+        block.
+      \item
+        {\bf Movement 25}, \emph{Annun so ap joomuk noollo makgi}, consist of
+        two blocks. The first is a ``pressing block with the left fore fist,''
+        and the second one is a ``side front block with the right inner
+        forearm.'' When searching, this movement will only register as one
+        block.
+    \end{itemize}
+
+    Movements 6, 7, 24 and 25 for pattern Po-Eun has the following tags
+    attached:
+
+  \begin{align*}
+    \{sitting\_stance, \: low\_technique, \: high\_technique, \\
+    left\_technique, \: right\_technique, \: block, \\
+    pressing\_block, fore\_fist, \: forearm, \: inner\_forearm, \\
+    side\_front\_block, \: continuous\_motion\}
+  \end{align*}
+
+  \item
+    \emph{Ge-Baek Tul}
+    \begin{itemize}
+      \item
+        The height of the kick in {\bf movement 23}, \emph{Twimyo yopcha
+        jirugi}, is not registered.
     \end{itemize}
   \item
-    \emph{Pragmatic}
+    \emph{Choong-Jang Tul}
     \begin{itemize}
       \item
-        Free software is available for experimentation and testing.
+        {\bf Movement 19}, \emph{Moorup najunde apcha busigi}, is tagged with
+        $\{front\_snap\_kick, \: knee\}$ which has an effect on the total of
+        low front snap kicks.
       \item
-        Most readers of this text have a background in relational technology. 
+        {\bf Movement 41}, \emph{Gunnun so sang sonkal soopyong taerigi}, is
+        tagged with $\{knife\_hand, \: twin\_knife\_hand\}$.
     \end{itemize}
@@
 
-\Section{Results}
+%\Section{Results}
 
@@
 
-\Section{Conclusions}
+%\Section{Conclusions}
 
@@
 % Unnumbered section (note the '*')
-\section*{Acknowledgments}
+%\section*{Acknowledgments}
 
@@
   % general feedback
-  Todo.
+  %Todo.
 

### 2010-12-26 bootstrap.rb
Fixed for Ruby 1.9.2

@@ -1,4 +1,5 @@
-require 'lab'
+require_relative 'lab'
+#require "/home/bjorn/scm/git/articles/left_arm_bias/lab.rb"
 
 # ----------------------------------------------------------------------
 # Database migration

### 2010-12-26 lab.rb

@@ -1,7 +1,5 @@
-require 'rubygems'
-
 # datamapper
-%w( dm-core dm-aggregates dm-validations ).each { |f| require f }
+%w( dm-core dm-aggregates dm-migrations dm-validations ).each { |f| require f }
 
 %w( pattern movement tag ).each do |model|
   load "#{Dir.pwd}/models/#{model}.rb"

### 2010-12-29 article.tex
Fixed wording on movement in Ge-Baek
Added comment regarding the conclusion
Is it possible to say something useful about *why* there are more
blocks with the left than with the right arm given the data set?
Added details to the approach, reworded the data section, plus minor fixes
    * Removed references to Wikipedia
    * Fixed quote reference
    * Fixed relevant examples
    * Removed tables with planned data regarding height
    * Added source to the Venn diagrams

@@
   or several imaginary opponents under various assumptions, using every
-  available attacking and blocking tool from different directions.
-  Furthermore, the techniques should also be evenly distributed between the
-  left and the right side\cite{cyclo:vol1}.
+  available attacking and blocking tool from different directions. In
+  addition, the techniques should also be evenly distributed between the left
+  and the right side\cite{cyclo:vol1}.
 
@@
 
-  In this article, therefore, we analyze hand techniques in patterns Chon-Ji
-  to Juche using tags and then report our findings of a left arm bias.
+  In this article we analyze hand techniques in patterns Chon-Ji to Juche
+  using tags, and then report our findings of a left arm bias.
 
@@
   keywords or labels that is attached to an object for later retrieval
-  \cite{golder:ct}\cite{huang:tt}\cite{shirky:ontology}\cite{wikipedia:tags}.
+  \cite{golder:ct}\cite{huang:tt}\cite{shirky:ontology}.
 
@@
 \SubSection{Set theory}
-  A \emph{set} is a collection of distinct objects. It is a plurality thought
-  of as a unit\cite{hausdorff:sets}. \emph{Set theory} is the branch of
-  mathematics that studies sets\cite{wikipedia:tags}.
+  A \emph{set} is a collection of distinct objects. It is ``a plurality
+  thought of as a unit''\cite{hausdorff:sets}. \emph{Set theory}, then, is the
+  branch of mathematics that studies sets.
 
@@
   $\{1,1,1\}$, however, is not a valid set because the element 1 occurs
-  repeatedly. Elements in a set can contain strings as well, so $\{loons,
-  terns, penguins\}$ is also a valid set.
+  repeatedly. Elements in a set can contain strings as well, so $\{blocks,
+  punches, strikes, thrusts\}$ is also a valid set.
 
@@
 
-  The terminology dataset is organized by pattern names. It contains a list of
-  all techniques in patterns Chon-Ji to Juche using terminology. It also
-  includes motion type on movements that are not performed in normal motion.
+  The dataset is organized by pattern names. It contains a list of all
+  techniques in patterns Chon-Ji to Juche. For each movement, the following
+  data has been registered:
 
-  The English description to every movement was registered manually after
-  reviewing, and making minor corrections to, the terminology.
+  \begin{enumerate}
+    \item Movement number
+    \item English description
+    \item Terminology
+    \item Tags
+  \end{enumerate}
 
@@
 
-  Each pattern movement is tagged on the basis of their English description
-  from the condensed encyclopedia. In addition, suitable tags were attached to
-  the dataset while performing the pattern to add necessary detail.
+  The movement number, together with the English description of each movement,
+  were registered manually from the condensed encyclopedia. After reviewing
+  and making minor corrections to the terminology data, it too was added.
+
+  Suitable tags were attached to every movement by first extracting keywords
+  from their English description, and second adding more detailed tags while
+  performing the pattern.
 
@@
   with the left forearm\cite{cyclo:vol1}.'' Removing the verbose parts of the
-  description we're left with:
+  description we are left with:
 
@@
 
-  Converting the above to tags gives us:
+  Supplementing the above with tags containing more information gives us:
 
@@
   Tagging movements in such a formalized manner, and registering it in a
-  database, enables us to retrieve the data we're interested in using concepts
-  from set theory.
+  database, enables us to retrieve the data we are interested in using
+  concepts from set theory.
 
@@
       \item
-        {\bf Movement 27}, \emph{Nachuo so sonbadak noollo makgi}, is tagged
-        as a $\{middle\_technique, \: low\_technique\}$ because the left hand
-        is in the middle section and the right hand, forming the pressing
-        block, is in the low section of the body. Furthermore, the movement
-        has been tagged as a $\{right\_technique, \: left\_technique\}$ to
-        reflect that both hands are being used.
+        {\bf Movement 27}, \emph{Nachuo so sonbadak noollo makgi}, is tagged as
+        a $\{middle\_technique, \: low\_technique\}$ because the left hand is
+        in the middle section and the right hand, forming the pressing block,
+        is in the low section of the body. The movement has, additionally, been
+        tagged as a $\{right\_technique, \: left\_technique\}$ to reflect that
+        both hands are being used.
       \item
-        {\bf Movement 29}, \emph{Nachuo so sonbadak noollo makgi}, is tagged
-        as a $\{middle\_technique, \: low\_technique\}$ because the right hand
-        is in the middle section and the left hand, forming the pressing
-        block, is in the low section of the body. Furthermore, the movement
-        has been tagged as a $\{right\_technique, \: left\_technique\}$ to
-        reflect that both hands are being used.
+        {\bf Movement 29}, \emph{Nachuo so sonbadak noollo makgi}, is tagged as
+        a $\{middle\_technique, \: low\_technique\}$ because the right hand is
+        in the middle section and the left hand, forming the pressing block, is
+        in the low section of the body. The movement has, additionally, been
+        tagged as a $\{right\_technique, \: left\_technique\}$ to reflect that
+        both hands are being used.
     \end{itemize}
@@
       \item
-        The height of the kick in {\bf movement 23}, \emph{Twimyo yopcha
-        jirugi}, is not registered.
+        {\bf Movement 23}, \emph{Twimyo yopcha jirugi}; the height of the kick
+        is not registered.
     \end{itemize}
@@
 
+% Is it possible to say anything about why there are more blocks with the left
+% hand, than with the right?
+
 % Unnumbered section (note the '*')
@@
   \end{table}
-
-\begin{table}
-  \centering
-  \begin{tabular}{l|c|c|c} \hline \hline
-    & High & Middle & Low \\ \hline
-
-    Blocks    & x   & y   & z \\
-    Punches   & x   & y   & z \\
-    Strikes   & x   & y   & z \\
-    Thrusts   & x   & y   & z \\
-    \hline
-
-  \end{tabular}
-  \caption{Total number of techniques by height.}
-  %\label{tab:table1}
-  \end{table}
-
-\begin{table}
-  \centering
-  \begin{tabular}{l|c|c|c} \hline \hline
-    & High & Middle & Low \\ \hline
-
-    Blocks    & x   & y   & z \\
-    Punches   & x   & y   & z \\
-    Strikes   & x   & y   & z \\
-    Thrusts   & x   & y   & z \\
-    \hline
-
-  \end{tabular}
-  \caption{Total number of techniques by height and arm.}
-  %\label{tab:table1}
-  \end{table}
-
-% percent more useful than numbers?
 
@@
 
-    \bibitem{wikipedia:sets}
-      \emph{Set theory}, July 19, 2010. \\
-      \url{http://en.wikipedia.org/wiki/Set_theory}
-
-    \bibitem{wikipedia:tags}
-      \emph{Tag (metadata)}, July 19, 2010. \\
-      \url{http://en.wikipedia.org/wiki/Tag}
-
 \end{thebibliography}

### 2010-12-30 article.tex
Added notes on classification

@@
     \{walking \: stance, \: left \: stance, \: low \: technique, \\
-    left \: technique, \: block, \: forearm, \: outer \: forearm, \\
-    normal \: motion\}
+    left \: technique, \: block, \: forearm, \\
+    outer \: forearm, normal \: motion\}
   \end{align*}
@@
 \begin{itemize}
+  \item
+    \emph{Do-San Tul}
+    \begin{itemize}
+      \item
+        {\bf Movement 13}, \emph{Gunnun so bakat palmok nopunde hechyo makgi},
+        is tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+       \item
+        {\bf Movement 17}, \emph{Gunnun so bakat palmok nopunde hechyo makgi},
+        is tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+    \end{itemize}
   \item
@@
       \item
+        {\bf Movement 13}, \emph{Gunnun so kyocha joomuk chukyo makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+      \item
         {\bf Movement 27}, \emph{Nachuo so sonbadak noollo makgi}, is tagged as
@@
         tagged as a $\{right\_technique, \: left\_technique\}$ to reflect that
-        both hands are being used.
+        two separate blocks are executed.
       \item
@@
         tagged as a $\{right\_technique, \: left\_technique\}$ to reflect that
-        both hands are being used.
+        two separate blocks are executed.
+    \end{itemize}
+  \item
+    \emph{Toi-Gae Tul}
+    \begin{itemize}
+      \item
+        {\bf Movement 7}, \emph{Gunnun so kyocha joomuk noollo makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+      \item
+        {\bf Movement 8}, \emph{Gunnun so sang joomuk nopunde sewo jirugi}, is
+        tagged as a left and right technique, with $\{left\_technique, \:
+        right\_technique\}$.
+      \item
+        {\bf Movement 20}, \emph{Gunnun sogi}, has only the stance registered
+        as part of the terminology though the English description says to
+        ``[e]xtend both hands upward as if to grab the opponent's head.''
+      \item
+        {\bf Movement 29}, \emph{Kyocha so kyocha joomuk noollo makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+    \end{itemize}
+  \item
+    \emph{Hwa-Rang Tul}
+    \begin{itemize}
+      \item
+        {\bf Movement 24}, \emph{Gunnun so kyocha joomuk noollo makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+    \end{itemize}
+  \item
+    \emph{Choong-Moo Tul}
+    \begin{itemize}
+      \item
+        {\bf Movement 11}, \emph{Gunnun sogi}, has only the stance registered
+        as part of the terminology though the English description says to
+        ``[e]xtend both hands upward as if to grab the opponent's head.''
+      \item
+        {\bf Movement 27}, \emph{Niunja so kyocha sonkal kaunde momcho makgi},
+        is tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+    \end{itemize}
+  \item
+    \emph{Kwang-Gae Tul}
+    \begin{itemize}
+      \item
+        {\bf Movement 21}, \emph{Nachuo so sonbadak noollo makgi}, is tagged as
+        a $\{middle\_technique, \: low\_technique\}$ because the right hand is
+        in the middle section and the left hand, forming the pressing block, is
+        in the low section of the body. The movement has, additionally, been
+        tagged as a $\{right\_technique, \: left\_technique\}$ to reflect that
+        two separate blocks are executed.
+      \item
+        {\bf Movement 22}, \emph{Nachuo so sonbadak noollo makgi}, is tagged as
+        a $\{middle\_technique, \: low\_technique\}$ because the right hand is
+        in the middle section and the left hand, forming the pressing block, is
+        in the low section of the body. The movement has, additionally, been
+        tagged as a $\{right\_technique, \: left\_technique\}$ to reflect that
+        two separate blocks are executed.
+      \item
+        {\bf Movement 31}, \emph{Gunnun so sang sewo jirugi}, is tagged as a
+        left and right technique, with $\{left\_technique, \:
+        right\_technique\}$.
+      \item
+        {\bf Movement 32}, \emph{Gunnun so sang joomuk dwijibo jirugi}, is
+        tagged as a left and right technique, with $\{left\_technique, \:
+        right\_technique\}$.
+      \item
+        {\bf Movement 36}, \emph{Gunnun so sang joomuk dwijibo jirugi}, is
+        tagged as a left and right technique, with $\{left\_technique, \:
+        right\_technique\}$.
     \end{itemize}
@@
       \item
+        {\bf Movement 8}, \emph{Annun so an palmok kaunde hechyo makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+      \item
         {\bf Movement 24}, \emph{Annun so ap joomuk noollo makgi}, consist of
@@
         block.
+      \item
+        {\bf Movement 26}, \emph{Annun so an palmok kaunde hechyo makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
     \end{itemize}
 
-    Movements 6, 7, 24 and 25 for pattern Po-Eun has the following tags
+    Movements 6, 7, 24 and 25 for pattern Po-Eun also have the following tags
     attached:
@@
     left\_technique, \: right\_technique, \: block, \\
-    pressing\_block, fore\_fist, \: forearm, \: inner\_forearm, \\
-    side\_front\_block, \: continuous\_motion\}
+    pressing\_block, fore\_fist, \: forearm, \\
+    inner\_forearm, \: side\_front\_block, \\
+    continuous\_motion\}
   \end{align*}
@@
       \item
-        {\bf Movement 23}, \emph{Twimyo yopcha jirugi}; the height of the kick
+        {\bf Movement 1}, \emph{Niunja so kyocha sonkal kaunde momcho makgi},
+        is tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+      \item
+        {\bf Movement 7}, \emph{Gunnun so nopunde doo bandalson makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+      \item
+        {\bf Movement 20}, \emph{Annun so gutja makgi}, is tagged as a left
+        and a right technique with $\{left\_technique, \: right\_technique\}$.
+        This increases the total amount of blocks on both sides.
+      \item
+        {\bf Movement 23}, \emph{Twimyo yopcha jirugi}, the height of the kick
         is not registered.
+      \item
+        {\bf Movement 24}, \emph{Gunnun so sang sewo jirugi}, is tagged as a
+        left and right technique, with $\{left\_technique, \:
+        right\_technique\}$.
+      \item
+        {\bf Movement 25}, \emph{Gunnun so nopunde doo bandalson makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+      \item
+        {\bf Movement 34}, \emph{Gunnun so sang sewo jirugi}, is tagged as a
+        left and right technique, with $\{left\_technique, \:
+        right\_technique\}$.
+      \item
+        {\bf Movement 36}, \emph{Annun so gutja makgi}, is tagged as a left
+        and a right technique with $\{left\_technique, \: right\_technique\}$.
+        This increases the total amount of blocks on both sides.
+    \end{itemize}
+  \item
+    \emph{Eui-Am Tul}
+    \begin{itemize}
+      \item
+        {\bf Movement 5}, \emph{Gunnun so kyocha joomuk naeryo makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+      \item
+        {\bf Movement 18}, \emph{Gunnun so kyocha joomuk naeryo makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+      \item
+        {\bf Movement 27}, \emph{Gunnun so sonkal kaunde hechyo makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+      \item
+        {\bf Movement 29}, \emph{Dwitbal so sang sonbadak naeryo makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+      \item
+        {\bf Movement 32}, \emph{Gunnun so sonkal kaunde hechyo makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+      \item
+        {\bf Movement 34}, \emph{Dwitbal so sang sonbadak naeryo makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
     \end{itemize}
@@
       \item
+        {\bf Movement 18}, \emph{Gunnun so kyocha joomuk noollo makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+      \item
         {\bf Movement 19}, \emph{Moorup najunde apcha busigi}, is tagged with
-        $\{front\_snap\_kick, \: knee\}$ which has an effect on the total of
-        low front snap kicks.
+        $\{front\_snap\_kick, \: knee\}$ because the English description says
+        to perform ``a low front snap kick to C with the right knee.'' This
+        has an effect on the total amount of low front snap kicks.
+      \item
+        {\bf Movement 24}, \emph{Dwitbal so sang sonbadak noollo makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+      \item
+        {\bf Movement 38}, \emph{Gunnun so bandae gutja makgi}, is tagged as a
+        left and a right technique with $\{left\_technique, \:
+        right\_technique\}$.  This increases the total amount of blocks on
+        both sides.
+      \item
+        {\bf Movement 40}, \emph{Gunnun so bandae gutja makgi}, is tagged as a
+        left and a right technique with $\{left\_technique, \:
+        right\_technique\}$.  This increases the total amount of blocks on
+        both sides.
       \item
@@
         tagged with $\{knife\_hand, \: twin\_knife\_hand\}$.
+    \end{itemize}
+  \item
+    \emph{Juche Tul}
+    \begin{itemize}
+      \item
+        {\bf Movement 1}, \emph{Annun so an palmok narani makgi}, is tagged as
+        left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on
+        both sides.
+      \item
+        {\bf Movement 4}, \emph{Waebal so bakat palmok narani makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, :\
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides. The movement also has the tag $\{parallel\_block\}$ attached to
+        it.
+      \item
+        {\bf Movement 13}, \emph{Annun so an palmok narani makgi}, is tagged
+        as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
+      \item
+        {\bf Movement 16}, \emph{Waebal so bakat palmok narani makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, :\
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides. The movement also has the tag $\{parallel\_block\}$ attached to
+        it.
+      \item
+        {\bf Movement 38}, \emph{Sasun so sang sonbadak chookyo makgi}, is
+        tagged as a left and a right technique with $\{left\_technique, \:
+        right\_technique\}$. This increases the total amount of blocks on both
+        sides.
     \end{itemize}

### 2011-01-01 article.tex
Added intro and special cases to Classification

@@
 
-  In this section we describe where the data originates, and then elaborate on
-  the approach taken to register and investigate the dataset.
+  In this section we describe where the data originates. Next we elaborate on
+  the approach taken to register and investigate the dataset. Finally, we have
+  a look at how each movement has been classified with emphasis on special
+  cases.
 
@@
   Suitable tags were attached to every movement by first extracting keywords
-  from their English description, and second adding more detailed tags while
+  from their English description, and then adding more detailed tags while
   performing the pattern.
@@
   with the left forearm\cite{cyclo:vol1}.'' Removing the verbose parts of the
-  description we are left with:
+  description leaves us with:
 
@@
 
-% TODO: introduction
+  Classification is done by attaching metadata, in terms of tags, to each
+  pattern movement. In most cases, applying tags to movements have been
+  straightforward. However, there are movements that need special mention.
+  These movements fall into two categories.
+
+  The first category consist of movements where both arms are part of the
+  technique by either forming the technique, or by being two separate
+  techniques in a single movement.
+
+  When both arms are used in one technique, the movement has been tagged with
+  $\{left\_technique, \: right\_technique\}$ to reflect that both arms are
+  needed for the technique, or that the movement contains two separate hand
+  techniques.
+
+  An example of a movement where both arms are required to form the technique
+  can be found in the 13\textsuperscript{th} movement of Joong-Gun Tul, which
+  is \emph{Gunnun so kyocha joomuk chukyo makgi}.
+
+  When it comes to a movement with two separate hand techniques, the
+  27\textsuperscript{th} movement of Joong-Gun Tul, being \emph{Nachuo so
+  sonbadak noollo makgi}, serves as a nice illustration.
+
+  The implications of tagging movements with $\{left\_technique, \:
+  right\_technique\}$ is that the total amount of hand techniques on either
+  side are higher than what actually is the case. This flaw does not affect
+  the bias we are investigating.
+
+  The second category comprises ambiguous movements, and thus contain
+  clarification on why certain tags were added.
+
+  Below is a list of all the special cases from both categories.
 
@@
         left and right technique, with $\{left\_technique, \:
-        right\_technique\}$.
+        right\_technique\}$. This increases the total amount of punches on
+        both sides.
       \item
@@
         a left and right technique, with $\{left\_technique, \:
-        right\_technique\}$.
+        right\_technique\}$. This increases the total amount of punches on
+        both sides.
       \item
@@
         tagged as a left and right technique, with $\{left\_technique, \:
-        right\_technique\}$.
+        right\_technique\}$. This increases the total amount of punches on
+        both sides.
       \item
@@
         tagged as a left and right technique, with $\{left\_technique, \:
-        right\_technique\}$.
+        right\_technique\}$. This increases the total amount of punches on
+        both sides.
     \end{itemize}

### 2011-01-02 article.tex
Removed directory example and rewrote tags section

@@
   one unambiguous category, which in turn is within another more general one.
-  Take the hierarchy of folders in a computer file system, for example. If we
-  want to organize articles on birds native to Africa in a directory, we have
-  several options:
 
-  \begin{lstlisting}
-    1. ~/articles/birds
-    2. ~/articles/africa
-    3. ~/articles/africa/birds
-    4. ~/articles/birds/africa
-  \end{lstlisting}
+  Take the hierarchy of folders in a computer file system, for example. How we
+  choose to organize the folders reflects a decision concerning the relative
+  importance of each characteristic\cite{golder:ct}.
 
-  How we choose to organize the folders reflects a decision concerning the
-  relative importance of each characteristic\cite{golder:ct}. Folder names and
-  levels are in themselves informative, in that, like tags, they describe the
-  information held within them\cite{jones:folders}.
-
-  The directory structure of (1), and (2) make central the fact that the
-  folders are about ``birds'' and ``africa''. But, they don't tell anything
-  about the other category. In (3) and (4) the files are organized by both
-  categories, and show that there is a parent-child or sibling relationships
-  between the folder names\cite{mathes:folk}.
+  Folder names are in themselves informative, in that, like tags, they
+  describe the information held within them\cite{jones:folders}. Furthermore,
+  they way folder names relate to each other show a structural relationship
+  between directories\cite{mathes:folk}.
 

### 2011-01-12 models/tag.rb
Added detailed comments on models

@@ -1,8 +1,51 @@
 class Tag
   include DataMapper::Resource
 
-  property :id,       Serial
-  property :name,     String, :required => true, :unique => true         # walking_stance, block, left_technique..
+  property :id,       Serial                                        # An auto-increment integer key.
+  property :name,     String, :required => true, :unique => true    # walking_stance, block, left_technique..
 
+  # Set up cardinality. That is, *how* one table links to another.
+  #
+  # Define that every tag has many movements.
   has n, :movements, :through => Resource
+
+  # Explanation of the 'has n, :movements, :through => Resource slightly
+  # adapted from http://datamapper.org/docs/associations
+  #
+  #   When auto_migrate! is being called, the model definitions above
+  #   will create a
+  #
+  #     MovementTag
+  #
+  #   model that will be automigrated and that will act as the join model.
+  #   DataMapper just picks both model names, sorts them alphabetically
+  #   and then joins them together. The resulting storage name follows
+  #   the  same conventions it would if the model had been declared
+  #   traditionally.
+  #
+  #   The resulting model is no different from any traditionally declared
+  #   model. It contains two belongs_to relationships pointing to both
+  #   Article and Category, and both underlying child key properties form
+  #   the composite primary key (CPK) of that model. DataMapper uses
+  #   consistent naming conventions to infer the names of the child key
+  #   properties. Since it's told to link together a Movement and a Tag
+  #   model, it'll establish the following relationships in the join
+  #   model:
+  #
+  #     MovementTag.belongs_to :movement, 'Movement', :key => true
+  #     MovementTag.belongs_to :tag,      'Tag',      :key => true
+  #
+  #   Since every many to many relationship needs a one to many
+  #   relationship to "go through", these also get set up for us.
+  #
+  #     Movement.has n, :movement_tags Tag.has n,     :movement_tags
+  #
+  #   Essentially, you can think of ":through => Resource" being replaced
+  #   with ":through => :movement_tags" when DM processes the relationship
+  #   definition.
+  #
+  #   This also means that you can access the join model just like any
+  #   other DataMapper model since there's really no difference at all.
+  #   All you need to know is the inferred name, then you can treat it
+  #   just like any other DataMapper model.
 end

### 2011-01-12 models/movement.rb
Added detailed comments on models

@@ -1,11 +1,67 @@
 class Movement
   include DataMapper::Resource
 
-  property :id,               Serial
-  property :number,           Integer,    :required => true     # The technique's movement number in the pattern
-  property :terminology,      Text,       :required => true     # Gunnun so bakat palmok najunde makgi
-  property :description,      Text,       :required => true     # Move the left foot to B, forming a left walking
-                                                                # ..stance toward B wile executing a middle punch
+  property :id,               Serial                                # An auto-increment integer key.
+  property :number,           Integer,    :required => true         # The technique's movement number in the pattern.
+  property :terminology,      Text,       :required => true         # Gunnun so bakat palmok najunde makgi.
+  property :description,      Text,       :required => true         # Move the left foot to B, forming a left walking stance toward B wile executing a middle punch.
+
+
+  # Declare the associations (ie. relationships) between models.
+  #
+  # With the associations defined, the models get a set of methods which
+  # enables us to create relationships and retrieve data from related
+  # models with DataMapper.
+  #
+  # Define that every movement belongs to a pattern by referencing the
+  # primary key in the patterns table as a foreign key in the movements
+  # table.
   belongs_to :pattern
+
+  # Set up cardinality. That is, *how* one table links to another.
+  #
+  # Define that every movement has and belongs to many tags. In other
+  # words, all movements have many tags, and many tags have many
+  # movements.
   has n, :tags, :through => Resource
+
+  # Explanation of the 'has n, :tags, :through => Resource slightly
+  # adapted from http://datamapper.org/docs/associations
+  #
+  #   When auto_migrate! is being called, the model definitions above
+  #   will create a
+  #
+  #     MovementTag
+  #
+  #   model that will be automigrated and that will act as the join model.
+  #   DataMapper just picks both model names, sorts them alphabetically
+  #   and then joins them together. The resulting storage name follows
+  #   the  same conventions it would if the model had been declared
+  #   traditionally.
+  #
+  #   The resulting model is no different from any traditionally declared
+  #   model. It contains two belongs_to relationships pointing to both
+  #   Article and Category, and both underlying child key properties form
+  #   the composite primary key (CPK) of that model. DataMapper uses
+  #   consistent naming conventions to infer the names of the child key
+  #   properties. Since it's told to link together a Movement and a Tag
+  #   model, it'll establish the following relationships in the join
+  #   model:
+  #
[…]

### 2011-01-12 models/pattern.rb

@@ -1,8 +1,11 @@
 class Pattern
   include DataMapper::Resource
 
-  property :id,               Serial
-  property :name,             String,     :unique => true
+  property :id,               Serial                                # An auto-increment integer key.
+  property :name,             String,     :unique => true           # Unique pattern name. No two values can be identical.
 
+  # Set up cardinality. That is, *how* one table links to another.
+  #
+  # Define that every pattern has many movements.
   has n, :movements
 end

### 2011-01-12 article.tex
Added more details to the approach section

@@
   The movement number, together with the English description of each movement,
-  were registered manually from the condensed encyclopedia. After reviewing
-  and making minor corrections to the terminology data, it too was added.
+  was registered manually from the condensed encyclopedia. After reviewing and
+  making minor corrections to the terminology, it too was added to the
+  dataset.
 
@@
   performing the pattern.
+
+  We then defined the data models with DataMapper, an Object Relational
+  Mapper\footnote{\url{http://www.datamapper.org}} (ORM) written in Ruby. The
+  models are Ruby classes with properties and associations. Properties define
+  field names and data types in the database, whereas the associations defines
+  the relationships and cardinality between the models.
+
+  Next we created a Ruby script that reads the dataset and automatically
+  populates the database. It sets up associations between models, and adds the
+  appropriate tags to every movement, as well as associations between movement
+  and pattern.
+
+  Tagging movements in such a formalized manner, and registering it in a
+  database, enables us to retrieve the data we are interested in using
+  concepts from set theory.
+
+\SubSection{Classification}
+
+  Classification is done by attaching metadata, in terms of tags, to each
+  pattern movement.
 
@@
 
-  Supplementing the above with tags containing more information gives us:
+  Supplementing the above with more detailed tags gives us:
 
@@
   Information about the stance type is presented first, followed by stance
-  side (left, right or none where applicable --- ie. sitting stance),
-  technique height (low, middle, high), technique side (left arm or right arm,
-  can also be both), direction of the technique (when needed), primary
-  technique type (attack, block, kick), technique group (punch, strike,
-  thrust), tool group (forearm, knife hand, finger etc.), tool (inner forearm,
-  outer forearm, double finger etc.), and finally motion type (normal motion,
-  slow motion, consecutive motion and so on).
+  side (left, right or none where applicable --- for example a sitting
+  stance), technique height (low, middle, high), technique side (left arm or
+  right arm, it can also be both), direction of the technique (when needed),
+  primary technique type (attack, block, kick), technique group (punch,
+  strike, thrust), tool group (forearm, knife hand, finger etc.), tool (inner
+  forearm, outer forearm, double finger etc.), and finally motion type (normal
+  motion, slow motion, consecutive motion and so on).
 
-  % FIXME add database and ruby script info here
-  % modelled the project in the database (./models)
-  %   explain all attributes etc.
-  % made a ruby script to parse the text files (link to bootstrap.rb ?)
-  %   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
-  %   saving the data into an sqlite3 database for analysis
-  %
-
-  Tagging movements in such a formalized manner, and registering it in a
-  database, enables us to retrieve the data we are interested in using
-  concepts from set theory.
-
-\SubSection{Classification}
-
-  Classification is done by attaching metadata, in terms of tags, to each
-  pattern movement. In most cases, applying tags to movements have been
-  straightforward. However, there are movements that need special mention.
-  These movements fall into two categories.
+  In most cases, applying tags to movements have been straightforward.
+  However, there are movements that need special mention.  These movements
+  fall into two categories.
 

### 2011-02-01 article.tex
Fixed table, added new table with values in percent
Added result section

@@
 
-\SubSection{Set theory}
+\SubSection{Set Theory}
   A \emph{set} is a collection of distinct objects. It is ``a plurality
@@
   right arm, it can also be both), direction of the technique (when needed),
-  primary technique type (attack, block, kick), technique group (punch,
+  primary technique type (attack, block, kick), technique group (block, punch,
   strike, thrust), tool group (forearm, knife hand, finger etc.), tool (inner
@@
 
-%\Section{Results}
+\Section{Results}
 
-%What's the answer? Specifically, most good computer architecture papers
-%conclude that something is so many percent faster, cheaper, smaller, or
-%otherwise better than something else. Put the result there, in numbers.
-%Avoid vague, hand-waving results such as ``very'', ``small'', or
-%``significant.''
+  Our findings show that of 519 techniques, 256 (49\%) are with the left arm
+  and 263 (51\%) with the right arm (Table \ref{tab:table1}). Looking at the
+  total amount of techniques, only 7 techniques (about 1\%) separates an even
+  distribution to both sides.
 
-%If you must be vague, you are only given license to do so when you can
-%talk about orders-of-magnitude improvement. There is a tension here in
-%that you should not provide numbers that can be easily misinterpreted,
-%but on the other hand you don't have room for all the caveats.
+%Techniques by
+  %tool group (forearm, knife hand, finger etc.)
+  %tool (inner forearm, outer forearm, double finger etc.)
 
-% Observation: Kicks happen between stances
-% Tables
-% Graphs
+\SubSection{Techniques by Groups}
+
+% what is the groups of techniques?
+
+  Table 2: Percent distribution by arm per category
+  Figures 1, 2, 3
+
+  In terms of category distribution, there are more blocks with the left side
+  than there are with the
+
+  It is worth noting that there are more blocks with the left side than with
+  the right side. That is, there are more attacks with the right arm than with
+  the left arm.
+
+\SubSection{Techniques by Patterns}
+
+\SubSection{Techniques by Stances}
+
+\SubSection{Techniques by Height}
+
+\SubSection{Techniques by Motion Type}
+
+\begin{table}
+  \centering
+  \begin{tabular}{l|r|r} \hline \hline
+    & Left Arm & Right Arm \\ \hline
+
+    Blocks    & 148   & 133 \\
+    Punches   &  60   &  71 \\
+    Strikes   &  34   &  38 \\
+    Thrusts   &  14   &  21 \\
+  \hline
+
+    \textbf{Total}   & \textbf{256}   & \textbf{263} \\
+    \hline
+  \end{tabular}
+  \caption{Number of techniques per arm by category.}
+  \label{tab:table1}
+  \end{table}
+
+\begin{table}
+  \centering
+  \begin{tabular}{l|r|r} \hline \hline
+    & Left Arm & Right Arm \\ \hline
+
+    Blocks    &  57.81\%    &  50.57\% \\
+    Punches   &  23.44\%    &  27.00\% \\
+    Strikes   &  13.28\%    &  14.45\% \\
+    Thrusts   &   5.47\%    &   7.98\% \\
+  \hline
+  \end{tabular}
+  \caption{Percent distribution of techniques per arm by category.}
+  \label{tab:table2}
+  \end{table}
+
+  \includegraphics[width=9cm]{all}
+  \includegraphics[width=9cm]{motion_type_all}
 
@@
 
-% Is it possible to say anything about why there are more blocks with the left
-% hand, than with the right?
+% Is it possible to say anything about why there are more blocks with the
+% right hand, than with the right?
+
+% Observation: Kicks happen between stances
+
+% Future research
+%   level of detail (ex. how each technique is divided per stance to say
+%   something about what stance is more suited for a technique, or to show a
+%   certain technique in a less/not used stance during step sparring to an
+%   understanding of techniques beyond patterns
 
@@
   %Todo.
-
-\begin{table}
-  \centering
-  \begin{tabular}{l|c|c} \hline \hline
-    & Left Arm & Right Arm \\ \hline
-
-    Blocks    & 148   & 133 \\
-    Punches   &  60   &  71 \\
-    Strikes   &  34   &  38 \\
-    Thrusts   &  21   &  14 \\
-    \hline
-
-    \textbf{Total}   & \textbf{263}   & \textbf{256} \\
-    \hline
-  \end{tabular}
-  \caption{Total number of techniques per arm by category.}
-  %\label{tab:table1}
-  \end{table}
 

### 2011-02-01 gnuplot_data.rb
Added gnuplot_data.rb

@@ -1,0 +1,3237 @@
+require 'RMagick'
+require 'gruff'
+require_relative 'lab'
+
+@left = Tag.first(:name => 'left_technique')
+@right = Tag.first(:name => 'right_technique')
+
+@high = Tag.first(:name => 'high_technique')
+@middle = Tag.first(:name => 'middle_technique')
+@low = Tag.first(:name => 'low_technique')
+
+@block = Tag.first(:name => 'block')
+@punch = Tag.first(:name => 'punch')
+@strike = Tag.first(:name => 'strike')
+@thrust = Tag.first(:name => 'thrust')
+
+@all_techniques = Movement.all
+@left_techniques = @left.movements.all
+@right_techniques = @right.movements.all
+
+@all_high = @high.movements.all
+@all_middle = @middle.movements.all
+@all_low = @low.movements.all
+
+@all_blocks = @block.movements.all
+@all_punches = @punch.movements.all
+@all_strikes = @strike.movements.all
+@all_thrusts = @thrust.movements.all
+
+@all_blocks_left = @all_blocks & @left_techniques
+@all_punches_left = @all_punches & @left_techniques
+@all_strikes_left = @all_strikes & @left_techniques
+@all_thrusts_left = @all_thrusts & @left_techniques
+
+@all_blocks_right = @all_blocks & @right_techniques
+@all_punches_right = @all_punches & @right_techniques
+@all_strikes_right = @all_strikes & @right_techniques
+@all_thrusts_right = @all_thrusts & @right_techniques
+
+# -----------------------------------------------------------------------------
+# All techniques
+# -----------------------------------------------------------------------------
+
+def all_techniques
+  all_blocks = @all_blocks_left.count + @all_blocks_right.count
+  all_punches = @all_punches_left.count + @all_punches_right.count
+  all_strikes = @all_strikes_left.count + @all_strikes_right.count
+  all_thrusts = @all_thrusts_left.count + @all_thrusts_right.count
+
+  puts "All techniques..."
+  dataset_all = [
+    [:blocks,
+      [
+        all_blocks,
+      ]
+    ],
+    [:punches,
+      [
+        all_punches,
+      ]
+    ],
+    [:strikes,
+      [
+        all_strikes,
+      ]
+    ],
+    [:thrusts,
+      [
+        all_thrusts,
+      ]
+    ],
+  ]
+
+  dataset_all.each { |data|
+    puts data[0], data[1]
+  }
+
[…]

### 2011-02-05 article.tex
Added gnuplot graphs

@@
 
-%Techniques by
-  %tool group (forearm, knife hand, finger etc.)
-  %tool (inner forearm, outer forearm, double finger etc.)
-
 \SubSection{Techniques by Groups}
 
-% what is the groups of techniques?
+% what are the groups of techniques?
 
   Table 2: Percent distribution by arm per category
-  Figures 1, 2, 3
 
@@
   the left arm.
-
-\SubSection{Techniques by Patterns}
-
-\SubSection{Techniques by Stances}
-
-\SubSection{Techniques by Height}
-
-\SubSection{Techniques by Motion Type}
 
@@
 
-  \includegraphics[width=9cm]{all}
-  \includegraphics[width=9cm]{motion_type_all}
+\SubSection{Techniques by Height}
+
+  % all techniques by height
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/height_all}
+    \caption{All techniques by height}
+    \label{fig:height_all}
+  \end{figure}
+
+  Techniques by height follow the same pattern when looking at all techniques,
+  as well as both sides. Most of the techniques are in the middle section,
+  except for strikes which there are more of in the high section. There are
+  very few punches, strikes and thrusts to the low section. In general, there
+  are more blocks than any other technique.
+
+\SubSection{Techniques by Patterns}
+
+  % all techniques by patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_all}
+    \caption{All techniques by patterns}
+    \label{fig:patterns_all}
+  \end{figure}
+
+  % left techniques by patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_left}
+    \caption{Left techniques by patterns}
+    \label{fig:patterns_left}
+  \end{figure}
+
+  % right techniques by patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_right}
+    \caption{Right techniques by patterns}
+    \label{fig:patterns_right}
+  \end{figure}
+
+  % all techniques by black belt patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_all}
+    \caption{All techniques by black belt patterns}
+    \label{fig:patterns_black_all}
+  \end{figure}
+
+  % left techniques by black belt patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_left}
+    \caption{Left techniques by black belt patterns}
+    \label{fig:patterns_black_left}
+  \end{figure}
+
+  % right techniques by black belt patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_right}
+    \caption{Right techniques by black belt patterns}
+    \label{fig:patterns_black_right}
+  \end{figure}
+
+  % all techniques by color belt patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_all}
+    \caption{All techniques by color belt patterns}
+    \label{fig:patterns_color_all}
+  \end{figure}
+
+  % left techniques by color belt patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_left}
+    \caption{Left techniques by color belt patterns}
+    \label{fig:patterns_color_left}
+  \end{figure}
+
+  % right techniques by color belt patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_right}
+    \caption{Right techniques by color belt patterns}
+    \label{fig:patterns_color_right}
+  \end{figure}
+
+\SubSection{Techniques by Stances}
+
+  % All techniques by stances
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_all}
+    \caption{All techniques by stances}
+    \label{fig:stances_all}
+  \end{figure}
+
+  % Left techniques by stances
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_left}
+    \caption{Left techniques by stances}
+    \label{fig:stances_left}
+  \end{figure}
+
+  % Right techniques by stances
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_right}
+    \caption{Right techniques by stances}
+    \label{fig:stances_right}
+  \end{figure}
+
+  % All techniques by stances except walking, sitting and L
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_not_wsl}
+    \caption{All techniques by stances except walking, sitting and L}
+    \label{fig:stances_not_wsl}
+  \end{figure}
+
+  % Left techniques by stances except walking, sitting and L
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_left_not_wsl}
+    \caption{Left techniques by stances except walking, sitting and L}
+    \label{fig:stances_left_not_wsl}
+  \end{figure}
+
+  % Right techniques by stances except walking, sitting and L
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_right_not_wsl}
+    \caption{Right techniques by stances except walking, sitting and L}
+    \label{fig:stances_right_not_wsl}
+  \end{figure}
+
+\SubSection{Techniques by Motion Type}
+
+  % all techniques by motion type
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_all}
+    \caption{All techniques by all motion types}
+    \label{fig:motion_all}
+  \end{figure}
+
+  Most techniques are normal motion, followed by fast motion and continuous
+  motion.
+
+  There are more motion types on the right side, than on the left. Right side
+  has flying motion and consecutive motion, whereas the left side does not.
+  There are more flying, slow, sliding and consecutive motions on the right
+  side. On the left side, there are more fast, stamping continuous and
+  connecting motions than on the right side.
+
+  There are equal amounts of slow, jumping, dodging, double stepping, shifting
+  motions on both sides, although with different groups of techniques.
+
+  % all techniques by motion type except normal motion
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_all_not_n}
+    \caption{All techniques by motion type except normal motion}
+    \label{fig:motion_all_not_n}
+  \end{figure}
+
+  % left techniques by motion type except normal motion
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_left_not_n}
+    \caption{Left techniques by motion type except normal motion}
+    \label{fig:motion_left_not_n}
+  \end{figure}
+
+  % right techniques by motion type except normal motion
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_right_not_n}
+    \caption{Right techniques by motion type except normal motion}
+    \label{fig:motion_right_not_n}
+  \end{figure}
 
@@
 
-% Is it possible to say anything about why there are more blocks with the
+% Is it possible to say anything about why there are more techniques with the
 % right hand, than with the right?

### 2011-02-06 article.tex
Moved tables 1 and 2 around

@@
 
-\SubSection{Techniques by Groups}
-
-% what are the groups of techniques?
-
-  Table 2: Percent distribution by arm per category
-
-  In terms of category distribution, there are more blocks with the left side
-  than there are with the
-
-  It is worth noting that there are more blocks with the left side than with
-  the right side. That is, there are more attacks with the right arm than with
-  the left arm.
-
   \begin{table}
@@
   \end{table}
+
+\SubSection{Techniques by Groups}
+
+  In terms of category distribution, there are more blocks with the left side
+  than there are with the right side. A side effect is that there are more
+  attacks with the right side, than with the left side (Table
+  \ref{tab:table2}).
 

### 2011-02-07 article.tex
Added graphs for all techniques, minor refactoring

@@
   in patterns Chon-Ji to Tong-Il. 85 kicks are with the right leg, and 67
-  kicks are with the left leg. This means that 56\% of the kicks are with the
-  right leg, and 44\% with the left leg.
+  kicks are with the left leg. This means that 56 \% of the kicks are with the
+  right leg, and 44 \% with the left leg.
 
@@
   Gibbs' paper, we find that there are 72 kicks in total. 42 kicks are with
-  the right leg, and 30 kicks are with the left leg. Roughly 58\% of the kicks
-  are with the right leg, and about 42\% with the left. Thus, the right leg
-  bias still holds.
+  the right leg, and 30 kicks are with the left leg. Roughly 58 \% of the
+  kicks are with the right leg, and about 42 \% with the left. Thus, the right
+  leg bias still holds.
 
@@
 
-  Our findings show that of 519 techniques, 256 (49\%) are with the left arm
-  and 263 (51\%) with the right arm (Table \ref{tab:table1}). Looking at the
-  total amount of techniques, only 7 techniques (about 1\%) separates an even
+  Our findings show that of 519 techniques, 256 (49 \%) are with the left arm
+  and 263 (51 \%) with the right arm (Table \ref{tab:table1}). Looking at the
+  total amount of techniques, only 7 techniques (about 1 \%) separates an even
   distribution to both sides.
@@
       Thrusts   &  14   &  21 \\
+
+      \hline
+      \textbf{Total}   & \textbf{256}   & \textbf{263} \\
       \hline
 
-      \textbf{Total}   & \textbf{256}   & \textbf{263} \\
-      \hline
     \end{tabular}
@@
   In terms of category distribution, there are more blocks with the left side
-  than there are with the right side. A side effect is that there are more
-  attacks with the right side, than with the left side (Table
-  \ref{tab:table2}).
+  than there are with the right side. There are, therefore, more attacks with
+  the right side, than with the left side (Table \ref{tab:table2}, Figure
+  \ref{fig:techniques_all}).
 
@@
 
-      Blocks    &  57.81\%    &  50.57\% \\
-      Punches   &  23.44\%    &  27.00\% \\
-      Strikes   &  13.28\%    &  14.45\% \\
-      Thrusts   &   5.47\%    &   7.98\% \\
+      Blocks    &  57.81 \%    &  50.57 \% \\
+      Punches   &  23.44 \%    &  27.00 \% \\
+      Strikes   &  13.28 \%    &  14.45 \% \\
+      Thrusts   &   5.47 \%    &   7.98 \% \\
+
       \hline
+      \textbf{Total}   & \textbf{100 \%}   & \textbf{100 \%} \\
+      \hline
+
     \end{tabular}
@@
   \end{table}
+
+  % Distribution of techniques by category
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/techniques_all}
+    \caption{Distribution of techniques by category.}
+    \label{fig:techniques_all}
+  \end{figure}
+
+\clearpage
 

### 2011-02-07 article.tex
Added description to techniques by height

@@
 
-\SubSection{Techniques by Groups}
+\SubSection{Techniques by Category}
 
-  In terms of category distribution, there are more blocks with the left side
-  than there are with the right side. There are, therefore, more attacks with
-  the right side, than with the left side (Table \ref{tab:table2}, Figure
-  \ref{fig:techniques_all}).
+  In terms of category distribution, there are more blocks on the left side
+  than there are on the right side. There are, therefore, more attacks on the
+  right side, than on the left side (Figure \ref{fig:techniques_all}, Table
+  \ref{tab:table2}).
+
+  Independent on side or total, all technique categories follow the same
+  pattern having most blocks, then punches, strikes and finally thrusts.
 
@@
 
-\clearpage
-
 \SubSection{Techniques by Height}
@@
 
-  Techniques by height follow the same pattern when looking at all techniques,
-  as well as both sides. Most of the techniques are in the middle section,
-  except for strikes which there are more of in the high section. There are
-  very few punches, strikes and thrusts to the low section. In general, there
-  are more blocks than any other technique.
+  Techniques by height follow the same trend when looking at all techniques
+  combined or techniques to either side. In general, there are more blocks
+  than any other technique. Most of the techniques are in the middle section,
+  although there is a greater occurrence of strikes in the high section, and
+  very few attacks in the low section.
 
@@
   \end{figure}
+
+\clearpage
 

### 2011-02-25 article.tex
Added content to techniques by motion type

@@
     \includegraphics[scale=0.72]{data/gnuplot/eps/height_all}
-    \caption{All techniques by height}
+    \caption{All techniques by height.}
     \label{fig:height_all}
@@
   Techniques by height follow the same trend when looking at all techniques
-  combined or techniques to either side. In general, there are more blocks
-  than any other technique. Most of the techniques are in the middle section,
-  although there is a greater occurrence of strikes in the high section, and
-  very few attacks in the low section.
-
-\SubSection{Techniques by Patterns}
-
-  % all techniques by patterns
-  \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_all}
-    \caption{All techniques by patterns}
-    \label{fig:patterns_all}
-  \end{figure}
-
-  % left techniques by patterns
-  \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_left}
-    \caption{Left techniques by patterns}
-    \label{fig:patterns_left}
-  \end{figure}
-
-  % right techniques by patterns
-  \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_right}
-    \caption{Right techniques by patterns}
-    \label{fig:patterns_right}
-  \end{figure}
-
-\clearpage
-
-  % all techniques by black belt patterns
-  \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_all}
-    \caption{All techniques by black belt patterns}
-    \label{fig:patterns_black_all}
-  \end{figure}
-
-  % left techniques by black belt patterns
-  \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_left}
-    \caption{Left techniques by black belt patterns}
-    \label{fig:patterns_black_left}
-  \end{figure}
-
-  % right techniques by black belt patterns
-  \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_right}
-    \caption{Right techniques by black belt patterns}
-    \label{fig:patterns_black_right}
-  \end{figure}
-
-  % all techniques by color belt patterns
-  \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_all}
-    \caption{All techniques by color belt patterns}
-    \label{fig:patterns_color_all}
-  \end{figure}
-
-  % left techniques by color belt patterns
-  \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_left}
-    \caption{Left techniques by color belt patterns}
-    \label{fig:patterns_color_left}
-  \end{figure}
-
-  % right techniques by color belt patterns
-  \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_right}
-    \caption{Right techniques by color belt patterns}
-    \label{fig:patterns_color_right}
-  \end{figure}
+  combined or techniques to either side (Figure \ref{fig:height_all}). In
+  general, there are more blocks than any other technique. Most of the
+  techniques are in the middle section, although there is a greater occurrence
+  of strikes in the high section, and very few attacks in the low section.
 
@@
 
-  % All techniques by stances
+  % All techniques by Walking, Sitting and L stances
   \begin{figure}
     \includegraphics[scale=0.72]{data/gnuplot/eps/stances_all}
-    \caption{All techniques by stances}
+    \caption{All techniques by walking, sitting and L stances.}
     \label{fig:stances_all}
@@
 
-  % Left techniques by stances
-  \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_left}
-    \caption{Left techniques by stances}
-    \label{fig:stances_left}
-  \end{figure}
+  Because most techniques are performed in walking, sitting and L stances, the
+  graphs in this section have been split into two groups. One group shows the
+  majority of techniques (84 \%), while the other visualize techniques in
+  every other stance (16 \%).
 
-  % Right techniques by stances
-  \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_right}
-    \caption{Right techniques by stances}
-    \label{fig:stances_right}
-  \end{figure}
+  When looking at all techniques by walking stances, sitting stances and L
+  stances (Figure \ref{fig:stances_all}), they roughly follow the same pattern
+  on both sides. There are, however, two minor exceptions. Firstly, there are
+  more strikes in L stances compared to walking stances on the left side.
+  Secondly, there are more punches than blocks to the right side.
 
-  % All techniques by stances except walking, sitting and L
+  % TODO All techniques by stances except walking, sitting and L stances
+  % show all techniques with *all* stances?
+
+  % All techniques by stances except walking, sitting and L stances
   \begin{figure}
     \includegraphics[scale=0.72]{data/gnuplot/eps/stances_not_wsl}
-    \caption{All techniques by stances except walking, sitting and L}
+    \caption{All techniques by stances except walking, sitting and L stances.}
     \label{fig:stances_not_wsl}
@@
     \includegraphics[scale=0.72]{data/gnuplot/eps/stances_left_not_wsl}
-    \caption{Left techniques by stances except walking, sitting and L}
+    \caption{Left techniques by stances except walking, sitting and L stances.}
     \label{fig:stances_left_not_wsl}
@@
     \includegraphics[scale=0.72]{data/gnuplot/eps/stances_right_not_wsl}
-    \caption{Right techniques by stances except walking, sitting and L}
+    \caption{Right techniques by stances except walking, sitting and L
+    stances.}
     \label{fig:stances_right_not_wsl}
@@
     \includegraphics[scale=0.72]{data/gnuplot/eps/motion_all}
-    \caption{All techniques by all motion types}
+    \caption{All techniques by all motion types.}
     \label{fig:motion_all}
@@
 
-  Most techniques are normal motion, followed by fast motion and continuous
-  motion.
-
-  There are more motion types on the right side, than on the left. Right side
-  has flying motion and consecutive motion, whereas the left side does not.
-  There are more flying, slow, sliding and consecutive motions on the right
-  side. On the left side, there are more fast, stamping continuous and
-  connecting motions than on the right side.
-
-  There are equal amounts of slow, jumping, dodging, double stepping, shifting
-  motions on both sides, although with different groups of techniques.
+  There are 14 different motion types registered in our data set. The larger
+  part of techniques (76 \%) are performed in normal motion (Figure
+  \ref{fig:motion_all}), followed by continuous motion (6 \%) and fast motion
+  (4 \%).
 
@@
     \includegraphics[scale=0.72]{data/gnuplot/eps/motion_all_not_n}
-    \caption{All techniques by motion type except normal motion}
+    \caption{All techniques by motion type except normal motion.}
     \label{fig:motion_all_not_n}
   \end{figure}
+
+  Excluding normal motion, it is interesting to note the high presence of
+  blocks in continuous motion, which alone amounts to 34 \% of blocks
+  performed (Figure \ref{fig:motion_all_not_n}). Continuing with Figure
+  \ref{fig:motion_all_not_n}, it shows that there is an abnormal number of
+  punches performed in fast motion compared to other motion types.
 
@@
     \includegraphics[scale=0.72]{data/gnuplot/eps/motion_left_not_n}
-    \caption{Left techniques by motion type except normal motion}
+    \caption{Left techniques by motion type except normal motion.}
     \label{fig:motion_left_not_n}
@@
     \includegraphics[scale=0.72]{data/gnuplot/eps/motion_right_not_n}
-    \caption{Right techniques by motion type except normal motion}
+    \caption{Right techniques by motion type except normal motion.}
     \label{fig:motion_right_not_n}
   \end{figure}
+
+  When examining the number of different motion types to either side, we find
+  that there are more motion types on the right side, than on the left. The
+  right side has flying motion and consecutive motion, in additon to motion
+  types found on the left side. Also, there are more flying, slow, sliding and
+  consecutive motions on the right side. However, there are more fast,
+  stamping, continuous and connecting motions on the left side. Comparing the
+  number of motion types on both sides reveals that there are equal amounts of
+  slow, jumping, dodging, double stepping and shifting motions, although with
+  different groups of techniques (Figures \ref{fig:motion_left_not_n},
+  \ref{fig:motion_right_not_n}.
+
+%\SubSection{Techniques by Patterns}
+
+  %% all techniques by patterns
+  %\begin{figure}
+    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_all}
+    %\caption{All techniques by patterns.}
+    %\label{fig:patterns_all}
+  %\end{figure}
+
+  %% left techniques by patterns
+  %\begin{figure}
+    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_left}
+    %\caption{Left techniques by patterns.}
+    %\label{fig:patterns_left}
+  %\end{figure}
+
+  %% right techniques by patterns
+  %\begin{figure}
+    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_right}
+    %\caption{Right techniques by patterns.}
+    %\label{fig:patterns_right}
+  %\end{figure}
+
+  %% all techniques by black belt patterns
+  %\begin{figure}
+    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_all}
+    %\caption{All techniques by black belt patterns.}
+    %\label{fig:patterns_black_all}
+  %\end{figure}
+
+  %% left techniques by black belt patterns
+  %\begin{figure}
+    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_left}
+    %\caption{Left techniques by black belt patterns.}
+    %\label{fig:patterns_black_left}
+  %\end{figure}
+
+  %% right techniques by black belt patterns
+  %\begin{figure}
+    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_right}
+    %\caption{Right techniques by black belt patterns.}
+    %\label{fig:patterns_black_right}
+  %\end{figure}
+
+  %% all techniques by color belt patterns
+  %\begin{figure}
+    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_all}
+    %\caption{All techniques by color belt patterns.}
+    %\label{fig:patterns_color_all}
+  %\end{figure}
+
+  %% left techniques by color belt patterns
+  %\begin{figure}
+    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_left}
+    %\caption{Left techniques by color belt patterns.}
+    %\label{fig:patterns_color_left}
+  %\end{figure}
+
+  %% right techniques by color belt patterns
+  %\begin{figure}
+    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_right}
+    %\caption{Right techniques by color belt patterns.}
+    %\label{fig:patterns_color_right}
+  %\end{figure}
 

### 2012-02-16 article.tex
Fixed wording and grammar

@@
 % Make the title bold
-\title{\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche}
+\title{\bf The Right Arm Bias in ITF Taekwon-Do \\ Patterns Chon-Ji to Juche}
 
@@
   In this article we analyze hand techniques in patterns Chon-Ji to Juche
-  using tags, and then report our findings of a left arm bias.
+  using tags, and then report our findings of a right arm bias.
 
@@
   describe the information held within them\cite{jones:folders}. Furthermore,
-  they way folder names relate to each other show a structural relationship
+  the way folder names relate to each other show a structural relationship
   between directories\cite{mathes:folk}.
@@
   In this section we describe where the data originates. Next we elaborate on
-  the approach taken to register and investigate the dataset. Finally, we have
-  a look at how each movement has been classified with emphasis on special
-  cases.
+  the approach taken to register and investigate the dataset. Finally, a look
+  at how each movement has been classified with emphasis on special cases.
 
@@
   We then defined the data models with DataMapper, an Object Relational
-  Mapper\footnote{\url{http://www.datamapper.org}} (ORM) written in Ruby. The
-  models are Ruby classes with properties and associations. Properties define
-  field names and data types in the database, whereas the associations defines
-  the relationships and cardinality between the models.
+  Mapper\footnote{\url{http://www.datamapper.org}} (ORM) written in the Ruby
+  programming language. The models are Ruby classes with properties and
+  associations. Properties define field names and data types in the database,
+  whereas the associations defines the relationships and cardinality between
+  the models.
 
@@
   27\textsuperscript{th} movement of Joong-Gun Tul, being \emph{Nachuo so
-  sonbadak noollo makgi}, serves as a nice illustration.
+  sonbadak noollo makgi}, serves as a good illustration.
 
@@
       \item
-        {\bf Movement 8}, \emph{Gunnun so sang joomuk nopunde sewo jirugi}, is
-        tagged as a left and right technique, with $\{left\_technique, \:
+        {\bf Movement 8}, \emph{Gunnun so sang sewo jirugi}, is tagged as a
+        left and right technique, with $\{left\_technique, \:
         right\_technique\}$. This increases the total amount of punches on
@@
       \item
-        {\bf Movement 20}, \emph{Gunnun sogi}, has only the stance registered
-        as part of the terminology though the English description says to
-        ``[e]xtend both hands upward as if to grab the opponent's head.''
+        {\bf Movement 20}, \emph{Gunnun so}, has only the stance registered
+        although the English description says to ``[e]xtend both hands upward
+        as if to grab the opponent's head.''
       \item
-        {\bf Movement 29}, \emph{Kyocha so kyocha joomuk noollo makgi}, is
+        {\bf Movement 29}, \emph{Gunnun so kyocha joomuk noollo makgi}, is
         tagged as a left and a right technique with $\{left\_technique, \:
@@
       \item
-        {\bf Movement 32}, \emph{Gunnun so sang joomuk dwijibo jirugi}, is
-        tagged as a left and right technique, with $\{left\_technique, \:
+        {\bf Movement 32}, \emph{Gunnun so sang dwijibo jirugi}, is tagged as
+        a left and right technique, with $\{left\_technique, \:
         right\_technique\}$. This increases the total amount of punches on
@@
       \item
-        {\bf Movement 36}, \emph{Gunnun so sang joomuk dwijibo jirugi}, is
-        tagged as a left and right technique, with $\{left\_technique, \:
+        {\bf Movement 36}, \emph{Gunnun so sang dwijibo jirugi}, is tagged as
+        a left and right technique, with $\{left\_technique, \:
         right\_technique\}$. This increases the total amount of punches on
@@
   Techniques by height follow the same trend when looking at all techniques
-  combined or techniques to either side (Figure \ref{fig:height_all}). In
-  general, there are more blocks than any other technique. Most of the
-  techniques are in the middle section, although there is a greater occurrence
-  of strikes in the high section, and very few attacks in the low section.
+  combined or techniques to either side. In general, there are more blocks
+  than any other technique. Most of the techniques are in the middle section,
+  although there is a greater occurrence of strikes in the high section, and
+  very few attacks in the low section (Figure \ref{fig:height_all}).
 
@@
   graphs in this section have been split into two groups. One group shows the
-  majority of techniques (84 \%), while the other visualize techniques in
-  every other stance (16 \%).
+  majority of techniques (84 \%), while the other visualize techniques
+  performed in the remaining stances (16 \%).
 
@@
   There are 14 different motion types registered in our data set. The larger
-  part of techniques (76 \%) are performed in normal motion (Figure
+  part of the techniques (76 \%) are performed in normal motion (Figure
   \ref{fig:motion_all}), followed by continuous motion (6 \%) and fast motion
@@
 % Is it possible to say anything about why there are more techniques with the
-% right hand, than with the right?
+% right hand, than with the left?
 
@@
 %   understanding of techniques beyond patterns
+
+% {left_technique, right_technique} should probably have been tagged
+% {both_hands} as well.
+
+% Link to the source code.
+
+% Movements with several blocks should have a tag indicating that there are
+% more than one block in the movement.
 

### 2012-02-16 article.tex
Fixed \notin
Fixed wording and grammar

@@
   $a \in S$ denotes that the object $a$ is a member of the set $S$. If $a$
-  is not a member of S, we write $a \not \in S$.
+  is not a member of S, we write $a \notin S$.
 
@@
   \[
-    S - T = \{x:x \in S \: and \: x \not \in T\}
+    S - T = \{x:x \in S \: and \: x \notin T\}
   \]
@@
   \[
-    S \Delta T = \{x:(x \in S \: and \: x \not \in T) \: or \: (x \in T \: and
-    \: x \not \in S)\}
+    S \Delta T = \{x:(x \in S \: and \: x \notin T) \: or \: (x \in T \: and
+    \: x \notin S)\}
   \]
@@
   In this section we describe where the data originates. Next we elaborate on
-  the approach taken to register and investigate the dataset. Finally, a look
+  the approach taken to register and investigate the dataset. Finally, we look
   at how each movement has been classified with emphasis on special cases.
@@
 
-  Suitable tags were attached to every movement by first extracting keywords
-  from their English description, and then adding more detailed tags while
-  performing the pattern.
+  Suitable tags were then attached to every movement by first extracting
+  keywords from their English description, and then adding more detailed tags
+  while performing the pattern.
 
@@
 
-  Classification is done by attaching metadata, in terms of tags, to each
+  Classification was done by attaching metadata, in terms of tags, to each
   pattern movement.
@@
   side are higher than what actually is the case. This flaw does not affect
-  the bias we are investigating.
+  the bias we are investigating, though.
 

### 2012-02-17 article.tex
Finished section on stances

@@
 
-  % TODO All techniques by stances except walking, sitting and L stances
-  % show all techniques with *all* stances?
-
   % All techniques by stances except walking, sitting and L stances
@@
   \end{figure}
+
+  When we look at all techniques excluding the frequently used walking,
+  sitting and L stances (Figure \ref{fig:stances_not_wsl}), we find that there
+  is an even distribution of techniques except for the closed stance, the
+  fixed stance and the vertical stance, which have more techniques to the
+  right side (Figure \ref{fig:stances_left_not_wsl} than to the left (Figure
+  \ref{fig:stances_right_not_wsl}.
 
@@
   \end{figure}
+
+  There are some additional stances which needs special mentioning. The close
+  stance is the only stance used by blocks, punches, strikes and thrusts. The
+  parallel stance is only used for punches, whereas the vertical stance is
+  only used for strikes. Only blocks are performed in the diagonal stance and
+  the bending ready stance A. And finally, there are no techniques on the left
+  side performed in the vertical stance.
+
+  The total amount of techniques for both sides are 37 blocks and 34 attacks.
+  Of all techniques on the left side, 59.5 \% are blocks, 40.46 \% are
+  attacks. This means that there are 19.05 \% more blocks than attacks
+  performed on that side. The right side follows the same pattern as the left,
+  with more blocks than attacks. 57.51 \% of techniqes are blocks and 42.6 \%
+  are attacks, meaning that there are 14.91 \% more blocks than attacks on the
+  right side.
 

### 2012-02-22 article.tex
Added content to techniques by patterns

@@
   fixed stance and the vertical stance, which have more techniques to the
-  right side (Figure \ref{fig:stances_left_not_wsl} than to the left (Figure
-  \ref{fig:stances_right_not_wsl}.
+  right side (Figure \ref{fig:stances_left_not_wsl}) than to the left (Figure
+  \ref{fig:stances_right_not_wsl}).
 
@@
   only used for strikes. Only blocks are performed in the diagonal stance and
-  the bending ready stance A. And finally, there are no techniques on the left
+  the bending ready stance A. Finally, there are no techniques on the left
   side performed in the vertical stance.
@@
   that there are more motion types on the right side, than on the left. The
-  right side has flying motion and consecutive motion, in additon to motion
+  right side has flying motion and consecutive motion, in addition to motion
   types found on the left side. Also, there are more flying, slow, sliding and
@@
 
-%\SubSection{Techniques by Patterns}
-
-  %% all techniques by patterns
+\SubSection{Techniques by Patterns}
+
+  With a few exceptions, all techniques by all patterns for both sides, follow
+  the same trend, where there are most blocks, then there are more punches
+  than strikes, and more strikes than thrusts (Figure \ref{fig:patterns_all}).
+
+  % all techniques by patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_all}
+    \caption{All techniques by patterns.}
+    \label{fig:patterns_all}
+  \end{figure}
+
+  The exceptions for all techniques on both sides are: Chon-Ji (having more
+  blocks than punches), Choong-Moo, Choong-Jang and Juche (with more punches
+  than strikes) and Po-Eun (where there are more strikes than thrusts).
+
+  % left techniques by patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_left}
+    \caption{Left techniques by patterns.}
+    \label{fig:patterns_left}
+  \end{figure}
+
+  % right techniques by patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_right}
+    \caption{Right techniques by patterns.}
+    \label{fig:patterns_right}
+  \end{figure}
+
+  There are, however, patterns which don't follow the exceptions described
+  above (Figures \ref{fig:patterns_left}, \ref{fig:patterns_right}). There
+  are, for instance, more punches than blocks in patterns Chon-Ji and Dan-Gun
+  on the right side than there are on the left side. And, when we compare the
+  number of punches to strikes, both Toi-Gae and Choong-Moo have an equal
+  amount of punches and strikes on the left side. Lastly, there is Choong-Jang
+  with more strikes than punches on the right side.
+
+  \subsubsection{Colored Belt Patterns}
+
+  % all techniques by color belt patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_all}
+    \caption{All techniques by color belt patterns.}
+    \label{fig:patterns_color_all}
+  \end{figure}
+
+  % left techniques by color belt patterns
   %\begin{figure}
-    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_all}
-    %\caption{All techniques by patterns.}
-    %\label{fig:patterns_all}
+    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_left}
+    %\caption{Left techniques by color belt patterns.}
+    %\label{fig:patterns_color_left}
   %\end{figure}
 
-  %% left techniques by patterns
+  % right techniques by color belt patterns
   %\begin{figure}
-    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_left}
-    %\caption{Left techniques by patterns.}
-    %\label{fig:patterns_left}
+    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_right}
+    %\caption{Right techniques by color belt patterns.}
+    %\label{fig:patterns_color_right}
   %\end{figure}
 
-  %% right techniques by patterns
-  %\begin{figure}
-    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_right}
-    %\caption{Right techniques by patterns.}
-    %\label{fig:patterns_right}
-  %\end{figure}
-
-  %% all techniques by black belt patterns
-  %\begin{figure}
-    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_all}
-    %\caption{All techniques by black belt patterns.}
-    %\label{fig:patterns_black_all}
-  %\end{figure}
-
-  %% left techniques by black belt patterns
+  \subsubsection{Black Belt Patterns}
+
+  % all techniques by black belt patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_all}
+    \caption{All techniques by black belt patterns.}
+    \label{fig:patterns_black_all}
+  \end{figure}
+
+  % left techniques by black belt patterns
   %\begin{figure}
@@
 
-  %% right techniques by black belt patterns
+  % right techniques by black belt patterns
   %\begin{figure}
@@
     %\label{fig:patterns_black_right}
-  %\end{figure}
-
-  %% all techniques by color belt patterns
-  %\begin{figure}
-    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_all}
-    %\caption{All techniques by color belt patterns.}
-    %\label{fig:patterns_color_all}
-  %\end{figure}
-
-  %% left techniques by color belt patterns
-  %\begin{figure}
-    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_left}
-    %\caption{Left techniques by color belt patterns.}
-    %\label{fig:patterns_color_left}
-  %\end{figure}
-
-  %% right techniques by color belt patterns
-  %\begin{figure}
-    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_right}
-    %\caption{Right techniques by color belt patterns.}
-    %\label{fig:patterns_color_right}
   %\end{figure}

### 2012-02-24 article.tex
Removed sections and figures for black and colored belts
Added abstract

@@
 
-%An academic abstract typically outlines four elements germane to the completed work:
-
-    %* The research focus (i.e. statement of the problem(s)/research issue(s) addressed);
-    %* The research methods used (experimental research, case studies, questionnaires, etc.);
-    %* The results/findings of the research; and
-    %* The main conclusions and recommendations
-
-  Todo.
+  When performing patterns in ITF Taekwon-Do, one of the factors mentioned in
+  the encyclopedia is that there should be an equal amount of techniques to
+  both sides of the body. Here we analyze hand techniques in Chon-Ji through
+  Juche to establish whether or not there is a bias towards either side.  This
+  is done by attaching metadata, in form of tags, to each pattern movement.
+  These tags are extracted from each movement's English description in the
+  condensed encyclopedia, and supplemented with keywords noted while
+  performing the pattern. We then apply concepts from set theory to retrieve
+  information we are interested in, and find that there are seven more
+  techniques on the right side than on the left.
+
 \end{em}
@@
 
-  \subsubsection{Colored Belt Patterns}
-
-  % all techniques by color belt patterns
-  \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_all}
-    \caption{All techniques by color belt patterns.}
-    \label{fig:patterns_color_all}
-  \end{figure}
-
-  % left techniques by color belt patterns
-  %\begin{figure}
-    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_left}
-    %\caption{Left techniques by color belt patterns.}
-    %\label{fig:patterns_color_left}
-  %\end{figure}
-
-  % right techniques by color belt patterns
-  %\begin{figure}
-    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_right}
-    %\caption{Right techniques by color belt patterns.}
-    %\label{fig:patterns_color_right}
-  %\end{figure}
-
-  \subsubsection{Black Belt Patterns}
-
-  % all techniques by black belt patterns
-  \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_all}
-    \caption{All techniques by black belt patterns.}
-    \label{fig:patterns_black_all}
-  \end{figure}
-
-  % left techniques by black belt patterns
-  %\begin{figure}
-    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_left}
-    %\caption{Left techniques by black belt patterns.}
-    %\label{fig:patterns_black_left}
-  %\end{figure}
-
-  % right techniques by black belt patterns
-  %\begin{figure}
-    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_right}
-    %\caption{Right techniques by black belt patterns.}
-    %\label{fig:patterns_black_right}
-  %\end{figure}
-
 %\Section{Conclusions}

### 2012-02-24 article.tex
Added conclusions
Readded figures for color belt and black belt patterns

@@
   than strikes, and more strikes than thrusts (Figure \ref{fig:patterns_all}).
+  This trend is also true when grouping the patterns by black belt patterns
+  and color belt patterns (Figures \ref{fig:patterns_black_all},
+  \ref{fig:patterns_color_all}).
 
@@
 
+  % all techniques by black belt patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_all}
+    \caption{All techniques by black belt patterns.}
+    \label{fig:patterns_black_all}
+  \end{figure}
+
+  % all techniques by color belt patterns
+  \begin{figure}
+    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_all}
+    \caption{All techniques by color belt patterns.}
+    \label{fig:patterns_color_all}
+  \end{figure}
+
   The exceptions for all techniques on both sides are: Chon-Ji (having more
-  blocks than punches), Choong-Moo, Choong-Jang and Juche (with more punches
-  than strikes) and Po-Eun (where there are more strikes than thrusts).
+  punches than blocks ), Choong-Moo, Choong-Jang and Juche (with more strikes
+  than punches) and Po-Eun (where there are more thrusts than strikes).
 
@@
 
-%\Section{Conclusions}
+\Section{Conclusions}
 
-%What are the implications of your answer? Is it going to change the
-%world (unlikely), be a significant ``win'', be a nice hack, or simply
-%serve as a road sign indicating that this path is a waste of time (all
-%of the previous results are useful). Are your results general,
-%potentially generalizable, or specific to a particular case?
-
-% Is it possible to say anything about why there are more techniques with the
-% right hand, than with the left?
-
-% Observation: Kicks happen between stances
+  There are more hand techniques performed on the right side than on the left
+  side. Thusly, there is a bias towards the right side.
 

### 2012-02-24 article.tex
Reduced size on figures

@@
   \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/techniques_all}
+    \includegraphics[scale=0.65]{data/gnuplot/eps/techniques_all}
     \caption{Distribution of techniques by category.}
@@
   \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/height_all}
+    \includegraphics[scale=0.65]{data/gnuplot/eps/height_all}
     \caption{All techniques by height.}
@@
   \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_all}
+    \includegraphics[scale=0.65]{data/gnuplot/eps/stances_all}
     \caption{All techniques by walking, sitting and L stances.}
@@
   \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_not_wsl}
+    \includegraphics[scale=0.65]{data/gnuplot/eps/stances_not_wsl}
     \caption{All techniques by stances except walking, sitting and L stances.}
@@
   \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_left_not_wsl}
+    \includegraphics[scale=0.65]{data/gnuplot/eps/stances_left_not_wsl}
     \caption{Left techniques by stances except walking, sitting and L stances.}
@@
   \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_right_not_wsl}
+    \includegraphics[scale=0.65]{data/gnuplot/eps/stances_right_not_wsl}
     \caption{Right techniques by stances except walking, sitting and L
@@
   \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_all}
+    \includegraphics[scale=0.65]{data/gnuplot/eps/motion_all}
     \caption{All techniques by all motion types.}
@@
   \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_all_not_n}
+    \includegraphics[scale=0.65]{data/gnuplot/eps/motion_all_not_n}
     \caption{All techniques by motion type except normal motion.}
@@
   \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_left_not_n}
+    \includegraphics[scale=0.65]{data/gnuplot/eps/motion_left_not_n}
     \caption{Left techniques by motion type except normal motion.}
@@
   \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_right_not_n}
+    \includegraphics[scale=0.65]{data/gnuplot/eps/motion_right_not_n}
     \caption{Right techniques by motion type except normal motion.}
@@
   \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_all}
+    \includegraphics[scale=0.65]{data/gnuplot/eps/patterns_all}
     \caption{All techniques by patterns.}
@@
   \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_all}
+    \includegraphics[scale=0.65]{data/gnuplot/eps/patterns_black_all}
     \caption{All techniques by black belt patterns.}
@@
   \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_all}
+    \includegraphics[scale=0.65]{data/gnuplot/eps/patterns_color_all}
     \caption{All techniques by color belt patterns.}
@@
   \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_left}
+    \includegraphics[scale=0.65]{data/gnuplot/eps/patterns_left}
     \caption{Left techniques by patterns.}
@@
   \begin{figure}
-    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_right}
+    \includegraphics[scale=0.65]{data/gnuplot/eps/patterns_right}
     \caption{Right techniques by patterns.}

### 2012-02-25 article.tex
Added acknowledgements
Fixed spelling errors
Fixed spelling and grammar
Thanks Frøydis for your excellent feedback!

@@
   When performing patterns in ITF Taekwon-Do, one of the factors mentioned in
-  the encyclopedia is that there should be an equal amount of techniques to
-  both sides of the body. Here we analyze hand techniques in Chon-Ji through
-  Juche to establish whether or not there is a bias towards either side.  This
-  is done by attaching metadata, in form of tags, to each pattern movement.
-  These tags are extracted from each movement's English description in the
-  condensed encyclopedia, and supplemented with keywords noted while
+  the condensed Encyclopedia is that there should be an equal number of
+  techniques to both sides of the body. Here we analyze hand techniques in
+  Chon-Ji through Juche to establish whether or not there is a bias towards
+  either side.  This is done by attaching metadata, in the form of tags, to
+  each pattern movement. These tags are extracted from each movement's English
+  description in the Encyclopedia, and supplemented with keywords noted while
   performing the pattern. We then apply concepts from set theory to retrieve
-  information we are interested in, and find that there are seven more
+  the information we are interested in, and find that there are seven more
   techniques on the right side than on the left.
@@
   Combined in a pattern, it allows the student to systematically deal with one
-  or several imaginary opponents under various assumptions, using every
-  available attacking and blocking tool from different directions. In
-  addition, the techniques should also be evenly distributed between the left
-  and the right side\cite{cyclo:vol1}.
-
-  It has, however, recently been observed that a bias towards the right leg
-  exist. The study by Gibbs\cite{rlb} show that there is a total of 152 kicks
-  in patterns Chon-Ji to Tong-Il. 85 kicks are with the right leg, and 67
-  kicks are with the left leg. This means that 56 \% of the kicks are with the
-  right leg, and 44 \% with the left leg.
+  or several imaginary opponents using every available attacking and blocking
+  tool from different directions. In addition, the techniques should also be
+  evenly distributed between the left and the right side\cite{cyclo:vol1}.
+
+  It has, however, recently been observed that there is a bias towards the
+  right leg. The study by Gibbs\cite{rlb} show that there is a total of 152
+  kicks in patterns Chon-Ji to Tong-Il. 85 kicks are with the right leg, and
+  67 kicks are with the left leg. This means that 56 \% of the kicks are with
+  the right leg, and 44 \% with the left leg.
 
   The work by Gibbs focused on kicks in all patterns, whereas this article
-  examines patterns Chon-Ji to Juche. Looking at kicks in said patterns using
+  examines patterns Chon-Ji to Juche. Looking at kicks in these patterns using
   Gibbs' paper, we find that there are 72 kicks in total. 42 kicks are with
@@
 
-  In a hierarchical and exclusive classification system, each object belong in
-  one unambiguous category, which in turn is within another more general one.
+  In a hierarchical and exclusive classification system, each object belongs
+  to one unambiguous category, which in turn belongs within another more
+  general category.
 
@@
   describe the information held within them\cite{jones:folders}. Furthermore,
-  the way folder names relate to each other show a structural relationship
+  the way folder names relate to each other shows a structural relationship
   between directories\cite{mathes:folk}.
@@
   associations. Properties define field names and data types in the database,
-  whereas the associations defines the relationships and cardinality between
+  whereas the associations define the relationships and cardinality between
   the models.
@@
 
-  Classification was done by attaching metadata, in terms of tags, to each
+  Classification was done by attaching metadata, in the form of tags, to each
   pattern movement.
@@
   B, forming a left walking stance toward B while executing a low block to B
-  with the left forearm\cite{cyclo:vol1}.'' Removing the verbose parts of the
-  description leaves us with:
+  with the left forearm\cite{cyclo:vol1}.'' Removing the redundant parts of
+  the description leaves us with:
 
@@
 
-  In most cases, applying tags to movements have been straightforward.
-  However, there are movements that need special mention. These movements
-  fall into two categories.
-
-  The first category consist of movements where both arms are part of the
+  In most cases, applying tags to movements has been straightforward.
+  However, there are movements that need special mention. These movements fall
+  into two categories.
+
+  The first category consists of movements where both arms are part of the
   technique by either forming the technique, or by being two separate
@@
 
-  When both arms are used in one technique, the movement has been tagged with
-  $\{left\_technique, \: right\_technique\}$ to reflect that both arms are
-  needed for the technique, or that the movement contains two separate hand
-  techniques.
+  In cases where both arms are used in one technique, the movement has been
+  tagged with $\{left\_technique, \: right\_technique\}$ to reflect that both
+  arms are needed for the technique, or that the movement contains two
+  separate hand techniques.
 
@@
   The implications of tagging movements with $\{left\_technique, \:
-  right\_technique\}$ is that the total amount of hand techniques on either
+  right\_technique\}$ are that the total amount of hand techniques on either
   side are higher than what actually is the case. This flaw does not affect
@@
 
-  The second category comprises ambiguous movements, and thus contain
+  The second category comprises ambiguous movements, and thus contains
   clarification on why certain tags were added.
@@
         is tagged as a left and a right technique with $\{left\_technique, \:
-        right\_technique\}$. This increases the total amount of blocks on both
+        right\_technique\}$. This increases the total number of blocks on both
         sides.
@@
         left and right technique, with $\{left\_technique, \:
-        right\_technique\}$. This increases the total amount of punches on
+        right\_technique\}$. This increases the total number of punches on
         both sides.
@@
         a left and right technique, with $\{left\_technique, \:
-        right\_technique\}$. This increases the total amount of punches on
+        right\_technique\}$. This increases the total number of punches on
         both sides.
@@
         tagged as a left and a right technique with $\{left\_technique, \:
-        right\_technique\}$. This increases the total amount of blocks on both
+        right\_technique\}$. This increases the total number of blocks on both
         sides.
@@
       \item
-        {\bf Movement 6}, \emph{Annun so ap joomuk noollo makgi}, consist of
+        {\bf Movement 6}, \emph{Annun so ap joomuk noollo makgi}, consists of
         two blocks. The first is a ``pressing block with the left fore fist,''
@@
       \item
-        {\bf Movement 7}, \emph{Annun so ap joomuk noollo makgi}, consist of
+        {\bf Movement 7}, \emph{Annun so ap joomuk noollo makgi}, consists of
         two blocks. The first is a ``pressing block with the right fore
@@
         tagged as a left and a right technique with $\{left\_technique, \:
-        right\_technique\}$. This increases the total amount of blocks on both
-        sides.
-      \item
-        {\bf Movement 24}, \emph{Annun so ap joomuk noollo makgi}, consist of
+        right\_technique\}$. This increases the total number of blocks on both
+        sides.
+      \item
+        {\bf Movement 24}, \emph{Annun so ap joomuk noollo makgi}, consists of
         two blocks. The first is a ``pressing block with the right fore
@@
       \item
-        {\bf Movement 25}, \emph{Annun so ap joomuk noollo makgi}, consist of
+        {\bf Movement 25}, \emph{Annun so ap joomuk noollo makgi}, consists of
         two blocks. The first is a ``pressing block with the left fore fist,''
@@
         and a right technique with $\{left\_technique, \: right\_technique\}$.
-        This increases the total amount of blocks on both sides.
+        This increases the total number of blocks on both sides.
       \item
@@
         and a right technique with $\{left\_technique, \: right\_technique\}$.
-        This increases the total amount of blocks on both sides.
+        This increases the total number of blocks on both sides.
     \end{itemize}
@@
         to perform ``a low front snap kick to C with the right knee.'' This
-        has an effect on the total amount of low front snap kicks.
+        has an effect on the total number of low front snap kicks.
       \item
@@
         left and a right technique with $\{left\_technique, \:
-        right\_technique\}$.  This increases the total amount of blocks on
+        right\_technique\}$.  This increases the total number of blocks on
         both sides.
@@
         left and a right technique with $\{left\_technique, \:
-        right\_technique\}$. This increases the total amount of blocks on
-        both sides.
+        right\_technique\}$. This increases the total number of blocks on both
+        sides.
       \item
@@
         tagged as a left and a right technique with $\{left\_technique, :\
-        right\_technique\}$. This increases the total amount of blocks on both
+        right\_technique\}$. This increases the total number of blocks on both
         sides. The movement also has the tag $\{parallel\_block\}$ attached to
@@
         as a left and a right technique with $\{left\_technique, \:
-        right\_technique\}$. This increases the total amount of blocks on both
+        right\_technique\}$. This increases the total number of blocks on both
         sides.
@@
   In terms of category distribution, there are more blocks on the left side
-  than there are on the right side. There are, therefore, more attacks on the
-  right side, than on the left side (Figure \ref{fig:techniques_all}, Table
+  than on the right side. There are, therefore, more attacks on the right
+  side, than on the left side (Figure \ref{fig:techniques_all}, Table
   \ref{tab:table2}).
-
-  Independent on side or total, all technique categories follow the same
-  pattern having most blocks, then punches, strikes and finally thrusts.
 
@@
   Techniques by height follow the same trend when looking at all techniques
-  combined or techniques to either side. In general, there are more blocks
-  than any other technique. Most of the techniques are in the middle section,
-  although there is a greater occurrence of strikes in the high section, and
-  very few attacks in the low section (Figure \ref{fig:height_all}).
+  combined or techniques to either side. Most of the techniques are in the
+  middle section, although there is a greater occurrence of strikes in the
+  high section, and very few attacks in the low section (Figure
+  \ref{fig:height_all}).
 
@@
   graphs in this section have been split into two groups. One group shows the
-  majority of techniques (84 \%), while the other visualize techniques
+  majority of techniques (84 \%), while the other visualizes techniques
   performed in the remaining stances (16 \%).
@@
 
-  There are some additional stances which needs special mentioning. The close
-  stance is the only stance used by blocks, punches, strikes and thrusts. The
-  parallel stance is only used for punches, whereas the vertical stance is
-  only used for strikes. Only blocks are performed in the diagonal stance and
-  the bending ready stance A. Finally, there are no techniques on the left
-  side performed in the vertical stance.
-
-  The total amount of techniques for both sides are 37 blocks and 34 attacks.
+  There are some additional stances which needs special mentioning. The closed
+  stance is the only stance used for blocking, punching, striking and
+  thrusting. The parallel stance is only used for punching, whereas the
+  vertical stance is only used for striking. Only blocks are performed in the
+  diagonal stance and the bending ready stance A. Finally, there are no
+  techniques on the left side performed in the vertical stance.
+
+  The total number of techniques for both sides is 37 blocks and 34 attacks.
   Of all techniques on the left side, 59.5 \% are blocks, 40.46 \% are
@@
   performed on that side. The right side follows the same pattern as the left,
-  with more blocks than attacks. 57.51 \% of techniqes are blocks and 42.6 \%
+  with more blocks than attacks. 57.51 \% of techniques are blocks and 42.6 \%
   are attacks, meaning that there are 14.91 \% more blocks than attacks on the
@@
   performed (Figure \ref{fig:motion_all_not_n}). Continuing with Figure
-  \ref{fig:motion_all_not_n}, it shows that there is an abnormal number of
+  \ref{fig:motion_all_not_n}, it shows that there is a high occurence of
   punches performed in fast motion compared to other motion types.
@@
   different groups of techniques (Figures \ref{fig:motion_left_not_n},
-  \ref{fig:motion_right_not_n}.
+  \ref{fig:motion_right_not_n}).
 
@@
   With a few exceptions, all techniques by all patterns for both sides, follow
-  the same trend, where there are most blocks, then there are more punches
-  than strikes, and more strikes than thrusts (Figure \ref{fig:patterns_all}).
+  the same trend. There are more blocks than punches, more punches than
+  strikes, and more strikes than thrusts (Figure \ref{fig:patterns_all}).
   This trend is also true when grouping the patterns by black belt patterns
@@
 
-  There are, however, patterns which don't follow the exceptions described
+  There are, however, patterns which do not follow the exceptions described
   above (Figures \ref{fig:patterns_left}, \ref{fig:patterns_right}). There
@@
   There are more hand techniques performed on the right side than on the left
-  side. Thusly, there is a bias towards the right side.
+  side. Thus, there is a bias towards the right side.
 
@@
 % Unnumbered section (note the '*')
-%\section*{Acknowledgments}
+\section*{Acknowledgments}
+
+  Todo.
 

### 2012-02-26 article.tex
Fixed wording in the abstract

@@
   Chon-Ji through Juche to establish whether or not there is a bias towards
-  either side.  This is done by attaching metadata, in the form of tags, to
-  each pattern movement. These tags are extracted from each movement's English
-  description in the Encyclopedia, and supplemented with keywords noted while
-  performing the pattern. We then apply concepts from set theory to retrieve
-  the information we are interested in, and find that there are seven more
-  techniques on the right side than on the left.
+  either side.  This is done by attaching metadata, in the form of tags, to each
+  pattern movement. These tags are generated from the Encyclopedia's description
+  of the movements, and supplemented by keywords that were identified by
+  carefully examining each pattern. We then apply concepts from set theory to
+  retrieve the information we are interested in, and find that there are seven
+  more techniques on the right side than on the left.
 

### 2012-03-20 article.tex
Removed comments on future research
Added acknowledgements
Removed double spaces

@@
   67 kicks are with the left leg. This means that 56 \% of the kicks are with
-  the right leg, and 44 \% with the left leg.
+  the right leg, and 44 \% are with the left leg.
 
@@
 
-% Future research
-%   level of detail (ex. how each technique is divided per stance to say
-%   something about what stance is more suited for a technique, or to show a
-%   certain technique in a less/not used stance during step sparring to an
-%   understanding of techniques beyond patterns
-
-% {left_technique, right_technique} should probably have been tagged
-% {both_hands} as well.
-
-% Link to the source code.
-
-% Movements with several blocks should have a tag indicating that there are
-% more than one block in the movement.
-
 % Unnumbered section (note the '*')
@@
 
-  Todo.
-
-  % Thanks to Master Nicolaisen (VII. Dan) for pointing out that I already had
-  % found a problem statement when I was still looking for one
-  %
-  % Odd-Magne Hansen (III. Dan) for helping me with the terminology, and
-  % general feedback
-  %Todo.
+  I would like to thank Odd-Magne Hansen (III. Dan), Frøydis Morken and Eirik
+  Schwenke for helping me with reviewing and proof-reading the article.
 
